---
title: "Short versus prolonged antibiotic therapy for complicated urinary tract infection in kidney transplant recipients: a target trial emulation"
subtitle: "Statistical report"
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 4
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: true
    code-tools: true
    code-summary: "Open code"
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: "#2D2D31"
bibliography: ../references.bib
fontcolor: "#D1D1D1"
monobackgroundcolor: "#3B3B3B"
---

------------------------------------------------------------------------

```{r, echo=FALSE}
path <- '~/1_ticf_sec/722_PETV_emul_trial_analysis'

knitr::opts_chunk$set(collapse = TRUE)
knitr::opts_knit$set(root.dir = path)
```

Set the report appearance.

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.86em;
  border: 1px solid #ffffff; 
  padding: 9px; 
}

code{
    color: #EEE8AA; 
    background: #96464D
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}
```


{{< include ../README.md >}}

# Initiation

```{r}

setwd(path)
source("r/initiation.R")

palette_study <- c("#A65F35", "#AF607C", "#477DA0")
outcomes <- c("recurence_till_1M", "recurence_till_90D")
outcome_labels <- c(
  recurence_till_1M = "Within 30 days",
  recurence_till_90D = "Within 90 days"
)
```

## Functions

```{r}

save_plot <- function(plot_obj, plot_name, width, height) {
  assign(plot_name, plot_obj, envir = .GlobalEnv)
  figure_path <- file.path("gitignore/figures", paste0(plot_name, ".pdf"))
  if (!file.exists(figure_path)) {
    ggsave(
      figure_path,
      plot = plot_obj,
      device = cairo_pdf,
      width = width,
      height = height,
      units = "in"
    )
  }
  plot_obj
}

profile_or <- function(model) {
  terms <- setdiff(names(coef(model)), "(Intercept)")
  limits <- confint(model, parm = terms, level = 0.95)
  limits <- matrix(limits, ncol = 2)
  data.frame(
    term = terms,
    OR = exp(unname(coef(model)[terms])),
    lower = exp(limits[, 1]),
    upper = exp(limits[, 2])
  )
}

my_labels_dict <- c(
  "(Intercept)" = "Intercept",
  "ATB_sensitivity_per7" =
    "Duration of appropriate therapy, per additional week",
  "log2_ATB_sensitivity_duration" =
    "Duration of appropriate therapy, per doubling",
  "ATB_overall_per7" = "Overall duration of therapy, per additional week",
  "log2_ATB_duration_overall" = "Overall duration of therapy, per doubling",
  "ATB_sensitivity_duration" = "Duration of appropriate therapy, days",
  "ATB_duration_overall" = "Overall duration of therapy, days",
  "treatment_under14D" = "Appropriate therapy, <=13 vs. >13 days",
  "sex_female" = "Female sex",
  "age" = "Age, years",
  "age_by30y" = "Age, per 30 years",
  "TX_to_infection_months" = "Time from transplantation to infection, months",
  "log2_TX_to_infection" = "Time from transplantation, per doubling",
  "urology_acute" = "Acute urological complications",
  "stent_in_situ" = "Ureteral stent in situ",
  "bph_pca_subvesical_obstruction" =
    "Subvesical obstruction",
  "urethral_stricture" = "Urethral stricture",
  "renofunctional_obstruction" = "Obstruction risk factors",
  "past_urol_instrumentation" = "Past urological instrumentation",
  "diabetes_severe" = "Complicated diabetes mellitus",
  "diabetes" = "Diabetes mellitus",
  "mra_positive" = "Multidrug-resistant pathogen",
  "bad_response_early_worsening" = "Unfavourable clinical response",
  "hemoculture_positive" = "Positive blood culture",
  "profylaxis" = "Antibiotic prophylaxis",
  "severe_aki" = "Stage 2–3 AKI",
  "CRP_entry" = "CRP at entry, mg/L",
  "CRP_max" = "Maximum CRP, mg/L",
  "CRP_entry_by100" = "CRP at entry, per 100 mg/L",
  "CRP_max_by100" = "Maximum CRP, per 100 mg/L",
  "log2(CRP_entry)" = "CRP at entry, per doubling",
  "log2(CRP_max)" = "Maximum CRP, per doubling",
  "years_from2019" = "Calendar time, per year",
  "I(years_from2019/10)" = "Calendar time, per decade",
  "I(years_from2019 / 10)" = "Calendar time, per decade",
  "calendar_period" = "Calendar period",
  "calendar_period<=2016" = "Calendar period 2008–2016",
  "calendar_period2017-2021" = "Calendar period 2017–2021",
  "calendar_period>=2022" = "Calendar period 2022 onward",
  "immunosuppression_regimen" = "Immunosuppressive regimen",
  "immunosuppression_regimenother triple" =
    "Immunosuppression, other vs. standard triple",
  "immunosuppression_regimendual or single" =
    "Immunosuppression, dual or single vs. standard triple",
  "depletion_induction_or_rejection_treatment_6M" =
    "Depletion induction or rejection treatment within 6 months",
  "fever_before_planned_ATB_stop" = "Fever before planned end of therapy",
  "clinical_worsening_before_planned_ATB_stop" =
    "Clinical worsening before planned end of therapy",
  "urine_findings_worsening_before_planned_ATB_stop" =
    "Worsening urinary findings before planned end of therapy",
  "ATB_extension_CRP_dynamics" = "Therapy extended because of CRP dynamics",
  "ATB_extension_other_reason" =
    "Therapy extended for another documented reason",
  "ATB_extension_urologic_procedure" =
    "Therapy extended because of a urological procedure",
  "any_problem_D1_13" = "Any recorded reason for extending therapy",
  "fever_signs" = "Systemic infection symptoms",
  "dysuria_UroInfSigns" = "Urinary tract infection symptoms",
  "initial_agent_identified" = "Culture-positive UTI",
  "recurence_till_1M" = "Recurrence within 30 days",
  "recurence_till_90D" = "Recurrence within 90 days",
  "distance" = "Propensity score"
)

plot_labels_dict <- c(
  "ATB_sensitivity_per7" = "Therapy duration (per week)",
  "log2_ATB_sensitivity_duration" = "Therapy duration (per doubling)",
  "ATB_overall_per7" = "Overall duration (per week)",
  "log2_ATB_duration_overall" = "Overall duration (per doubling)",
  "ATB_sensitivity_duration" = "Therapy duration (days)",
  "ATB_duration_overall" = "Overall duration (days)",
  "treatment_under14D" = "Therapy duration (<=13 vs. >13 days)",
  "sex_female" = "Female sex",
  "age" = "Age (years)",
  "age_by30y" = "Age (per 30 years)",
  "TX_to_infection_months" = "Time since TX (months)",
  "log2_TX_to_infection" = "Time since TX (per doubling)",
  "urology_acute" = "Acute urological complications",
  "stent_in_situ" = "Ureteral stent",
  "bph_pca_subvesical_obstruction" = "Subvesical obstruction",
  "urethral_stricture" = "Urethral stricture",
  "renofunctional_obstruction" = "Obstruction risk factors",
  "past_urol_instrumentation" = "Past urological instrumentation",
  "diabetes_severe" = "Complicated diabetes",
  "diabetes" = "Diabetes",
  "mra_positive" = "MDR pathogen",
  "bad_response_early_worsening" = "Poor response/early worsening",
  "hemoculture_positive" = "Positive blood culture",
  "profylaxis" = "ATB prophylaxis",
  "severe_aki" = "Stage 2–3 AKI",
  "CRP_entry" = "Entry CRP (mg/L)",
  "CRP_max" = "Maximum CRP (mg/L)",
  "CRP_entry_by100" = "Entry CRP (per 100 mg/L)",
  "CRP_max_by100" = "Maximum CRP (per 100 mg/L)",
  "log2(CRP_entry)" = "Entry CRP (per doubling)",
  "log2(CRP_max)" = "Maximum CRP (per doubling)",
  "years_from2019" = "Calendar time (per year)",
  "I(years_from2019/10)" = "Calendar time (per decade)",
  "I(years_from2019 / 10)" = "Calendar time (per decade)",
  "calendar_period" = "Calendar period",
  "calendar_period<=2016" = "2008 to 2016",
  "calendar_period2017-2021" = "2017 to 2021",
  "calendar_period>=2022" = "2022 onward",
  "immunosuppression_regimen" = "Maintenance IS",
  "immunosuppression_regimenother triple" = "Other triple IS",
  "immunosuppression_regimendual or single" = "Dual or single IS",
  "depletion_induction_or_rejection_treatment_6M" =
    "Depletion/rejection treatment",
  "distance" = "Propensity score"
)

plot_my_model <- function(
  model,
  axis.lim = NULL,
  grid.breaks = NULL
) {
  model_terms <- names(coef(model))
  plot_terms <- model_terms[model_terms != "(Intercept)"]

  mapped_labels <- unname(ifelse(
    is.na(plot_labels_dict[plot_terms]),
    plot_terms,
    plot_labels_dict[plot_terms]
  ))

  sjPlot::plot_model(
    model,
    type = "est",
    title = "",
    axis.lim = axis.lim,
    grid.breaks = grid.breaks,
    axis.labels = stringr::str_wrap(
      rev(mapped_labels),
      width = 42
    )
  ) +
    geom_hline(
      yintercept = 1,
      linetype = "dashed",
      colour = "black"
    )
}
```

## Analysis data

The data and model formulas are retained. Table labels follow manuscript v12 and its supplement. Plot labels are shortened; figure captions define the abbreviations and treatment duration. Calendar time remains centred on the median overall treatment initiation date, as in the source code; the historical variable name years_from2019 does not imply centring on 2019.

```{r}

data_2017 <- data_analysis |>
  dplyr::filter(calendar_year >= 2017) |>
  data.frame()

analysis_data_check <- data_analysis |>
  dplyr::summarise(
    patients = dplyr::n(),
    missing_entry_CRP = sum(is.na(CRP_entry)),
    zero_entry_CRP = sum(CRP_entry == 0, na.rm = TRUE),
    zero_maximum_CRP = sum(CRP_max == 0, na.rm = TRUE)
  ) |>
  data.frame()
kableExtra::kable(
  analysis_data_check,
  caption = "Analysis data after loading or rebuilding the cache. patients is the cohort size; missing_entry_CRP and zero_entry_CRP count missing and zero entry CRP; zero_maximum_CRP counts zero maximum CRP. The supplied initiation recodes blank CRP as zero before its existing missing-entry-CRP filter; no new zero replacement is introduced here. Verify these counts when rebuilding the dataset"
)
```


# Descriptive analyses

## Calendar-year recurrence risk

```{r}
year_risk <- data_analysis |>
  dplyr::select(
    calendar_year,
    dplyr::all_of(outcomes)
  ) |>
  tidyr::pivot_longer(
    cols = dplyr::all_of(outcomes),
    names_to = "outcome"
  ) |>
  dplyr::filter(
    !is.na(calendar_year),
    !is.na(value)
  ) |>
  dplyr::group_by(
    calendar_year,
    outcome
  ) |>
  dplyr::summarise(
    n = dplyr::n(),
    events = sum(value),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    risk = events / n,
    z = qnorm(0.975),
    center = (risk + z^2 / (2 * n)) / (1 + z^2 / n),
    half_width = z * sqrt(risk * (1 - risk) / n +
    z^2 / (4 * n^2)) / (1 + z^2 / n),
    lower = center - half_width,
    upper = center + half_width,
    window = factor(outcome_labels[outcome], levels = outcome_labels)
  ) |>
  dplyr::select(
    calendar_year,
    window,
    n,
    events,
    risk,
    lower,
    upper
  ) |>
  data.frame()
kableExtra::kable(
  year_risk,
  digits = 3,
  caption = "Observed recurrence after therapy completion by calendar year. window identifies 30-day or 90-day follow-up; n is the number of patients and events the number with recurrence. risk is events divided by n; lower and upper are 95% Wilson confidence limits"
)
```

Plot the results

```{r, fig.height=5, fig.width=10}
#| fig-cap: "Figure 1. Observed recurrence within 30 and 90 days after therapy completion by calendar year of sensitivity ATB treatment initiation. Black points show observed proportions, grey vertical bars show 95% Wilson confidence intervals, and connecting lines guide the eye"

year_breaks <- seq(
  floor(min(year_risk$calendar_year) / 2) * 2,
  ceiling(max(year_risk$calendar_year) / 2) * 2,
  by = 2
)
myplot <- ggplot(year_risk, aes(calendar_year, risk)) +
  geom_line() +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "grey50") +
  geom_point() +
  facet_wrap(~ window) +
  scale_x_continuous(breaks = year_breaks, minor_breaks = NULL) +
  scale_y_continuous(labels = scales::label_percent()) +
  labs(
    x = "Calendar year at sensitivity ATB treatment initiation",
    y = "Recurrence risk"
  ) +
  theme(
    panel.grid.major.x = element_line(colour = "white"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
plotac <- "fig_x01"
myplot <- save_plot(myplot, plotac, width = 10, height = 5)
myplot
```

## Cohort description

Compare patient characteristics between the two treatment groups. Continuous variables are shown as median (interquartile range), and categorical variables as counts and percentages. Missing values are shown separately.

```{r}
cohort_table <- data_analysis |>
  dplyr::select(
    treatment_group,
    age,
    sex_female,
    TX_to_infection_months,
    urology_acute,
    stent_in_situ,
    bph_pca_subvesical_obstruction,
    urethral_stricture,
    renofunctional_obstruction,
    diabetes_severe,
    diabetes,
    mra_positive,
    bad_response_early_worsening,
    initial_agent_identified,
    hemoculture_positive,
    fever_signs,
    dysuria_UroInfSigns,
    profylaxis,
    severe_aki,
    CRP_entry,
    CRP_max,
    immunosuppression_regimen,
    depletion_induction_or_rejection_treatment_6M,
    calendar_period,
    ATB_sensitivity_duration,
    recurence_till_1M,
    recurence_till_90D
  ) |>
  data.frame() |>
  gtsummary::tbl_summary(
    by = treatment_group,
    label = list(
      age ~
        "Age, years",
      sex_female ~
        "Female sex",
      TX_to_infection_months ~
        "Time from transplantation to infection, months",
      urology_acute ~
        "Acute urological complications",
      stent_in_situ ~
        "Ureteral stent in situ",
      bph_pca_subvesical_obstruction ~
        "Subvesical obstruction",
      urethral_stricture ~
        "Urethral stricture",
      renofunctional_obstruction ~
        "Obstruction risk factors",
      diabetes_severe ~
        "Complicated diabetes mellitus",
      diabetes ~
        "Diabetes mellitus",
      mra_positive ~
        "Multidrug-resistant pathogen",
      bad_response_early_worsening ~
        "Unfavourable clinical response",
      initial_agent_identified ~
        "Culture-positive UTI",
      hemoculture_positive ~
        "Positive blood culture",
      fever_signs ~
        "Systemic infection symptoms",
      dysuria_UroInfSigns ~
        "Urinary tract infection symptoms",
      profylaxis ~
        "Antibiotic prophylaxis",
      severe_aki ~
        "Stage 2–3 AKI",
      CRP_entry ~
        "CRP at entry, mg/L",
      CRP_max ~
        "Maximum CRP, mg/L",
      immunosuppression_regimen ~
        "Immunosuppressive regimen",
      depletion_induction_or_rejection_treatment_6M ~
        "Depletion induction or rejection treatment within 6 months",
      calendar_period ~
        "Calendar period",
      ATB_sensitivity_duration ~
        "Duration of appropriate therapy, days",
      recurence_till_1M ~
        "Recurrence within 30 days",
      recurence_till_90D ~
        "Recurrence within 90 days"
    ),
    type = list(
      c(
        initial_agent_identified,
        hemoculture_positive,
        fever_signs,
        dysuria_UroInfSigns,
        recurence_till_1M,
        recurence_till_90D
      ) ~ "dichotomous"
    ),
    value = list(
      c(
        initial_agent_identified,
        hemoculture_positive,
        fever_signs,
        dysuria_UroInfSigns,
        recurence_till_1M,
        recurence_till_90D
      ) ~ 1
    ),
    statistic = list(
      gtsummary::all_continuous() ~ "{median} ({p25}, {p75})",
      gtsummary::all_categorical() ~ "{n} ({p}%)"
    ),
    missing = "ifany"
  ) |>
  gtsummary::bold_labels() |>
  gtsummary::modify_caption(
    "Patient characteristics by sensitivity ATB duration. Continuous variables are shown as median (interquartile range), and categorical variables as counts and within-group percentages among patients with available values. Binary variables show the number and percentage coded 1, indicating presence. Recurrence is measured within 30 and 90 days after therapy completion"
  )

cohort_table
```

## Correlations among continuous measures

Look for closely related measures before interpreting models that include them together. Spearman correlations describe rank relationships; the lower panels show the original observations.

```{r, fig.height=9, fig.width=9.5}
#| fig-cap: "Figure 2. Pairwise Spearman correlations among age, admission and maximum CRP, time since transplantation, and sensitivity ATB, overall and intravenous antibiotic duration. Upper cells show Spearman rho; lower cells show individual observations. Variables are ordered by UPGMA hierarchical clustering using distance 1 minus rho and average linkage. Pairwise complete records are used; axes in lower cells use each variable's observed range. Effective therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro. IV theraphy means intravenous antibiotic therapy. Overall duration includes all antibiotic treatment irrespective of in vitro susceptibility; IV denotes intravenous and TX transplantation"

correlation_data <- data_analysis |>
  dplyr::select(
    age,
    CRP_entry,
    CRP_max,
    TX_to_infection_months,
    ATB_sensitivity_duration,
    ATB_duration_overall,
    ATB_IV_duration
  ) |>
  data.frame()
correlation_labels <- c(
  "Age [years]", "Entry CRP [mg/L]", "Maximum CRP [mg/L]",
  "Time since TX [months]", "Effective therapy duration [days]",
  "Overall ATB duration [days]", "IV ATB duration [days]"
)
rho_matrix <- cor(
  correlation_data,
  method = "spearman",
  use = "pairwise.complete.obs"
)
correlation_upgma <- hclust(as.dist(1 - rho_matrix), method = "average")
correlation_order <- correlation_upgma$order
display_position <- integer(length(correlation_order))
display_position[correlation_order] <- seq_along(correlation_order)
rho_display <- rho_matrix
rho_display[!outer(display_position, display_position, "<")] <- NA_real_
myplot <- ComplexHeatmap::Heatmap(
  rho_display,
  name = "Spearman rho",
  col = circlize::colorRamp2(
    c(-1, 0, 1), c("#3B4CC0", "white", "#B40426")
  ),
  cluster_rows = FALSE,
  row_order = correlation_order,
  cluster_columns = as.dendrogram(correlation_upgma),
  column_dend_reorder = FALSE,
  show_row_dend = FALSE,
  row_labels = correlation_labels,
  column_labels = correlation_labels,
  column_names_rot = 55,
  column_dend_height = grid::unit(35, "mm"),
  na_col = "white",
  rect_gp = grid::gpar(col = "grey85"),
  cell_fun = function(j, i, x, y, width, height, fill) {
    if (display_position[i] < display_position[j]) {
      grid::grid.text(sprintf("%.2f", rho_matrix[i, j]), x, y)
    }
    if (display_position[i] > display_position[j]) {
      pairs <- correlation_data[, c(j, i)]
      pairs <- pairs[complete.cases(pairs), , drop = FALSE]
      grid::pushViewport(grid::viewport(
        x = x, y = y, width = width, height = height,
        xscale = range(pairs[[1]]), yscale = range(pairs[[2]]),
        clip = "on"
      ))
      grid::grid.rect(gp = grid::gpar(fill = "white", col = "grey85"))
      grid::grid.points(
        pairs[[1]], pairs[[2]], default.units = "native",
        pch = 16, size = grid::unit(1, "mm"),
        gp = grid::gpar(col = grDevices::rgb(0, 0, 0, alpha = 0.2))
      )
      grid::popViewport()
    }
  }
)
plotac <- "fig_x02"
assign(plotac, myplot)
figure_path <- file.path("gitignore/figures", paste0(plotac, ".pdf"))
if (!file.exists(figure_path)) {
  cairo_pdf(figure_path, width = 9.5, height = 9)
  ComplexHeatmap::draw(get(plotac))
  dev.off()
}
grid::grid.newpage()
ComplexHeatmap::draw(get(plotac))
```


# Unadjusted regression

Fit each predictor separately

```{r}
unadjusted_table <- function(outcome, predictors, data) {
  purrr::map_dfr(predictors, function(predictor) {
    model <- glm(
      reformulate(predictor, response = outcome),
      data = data,
      family = binomial(link = "logit")
    )
    profile_or(model) |>
      dplyr::mutate(
        predictor = predictor,
        term = dplyr::coalesce(unname(my_labels_dict[term]), term),
        n = nobs(model),
        .before = 1
      )
  }) |>
    data.frame()
}

unadjusted_predictors <- c(
  "ATB_sensitivity_per7", "log2_ATB_sensitivity_duration",
  "ATB_overall_per7", "log2_ATB_duration_overall",
  "treatment_under14D", "sex_female", "age_by30y",
  "log2_TX_to_infection", "urology_acute", "diabetes_severe",
  "mra_positive", "bad_response_early_worsening", "hemoculture_positive",
  "profylaxis", "severe_aki", "log2(CRP_entry)", "log2(CRP_max)",
  "I(years_from2019 / 10)", "immunosuppression_regimen",
  "depletion_induction_or_rejection_treatment_6M", "any_problem_D1_13"
)
```

## Recurrence within 30 days

Show the unadjusted associations

```{r}
unadjusted_30D <- unadjusted_table(
  "recurence_till_1M",
  unadjusted_predictors,
  data_analysis
)
kableExtra::kable(
  unadjusted_30D,
  digits = 3,
  caption = "Unadjusted associations with recurrence within 30 days after therapy completion. Each predictor was fitted separately using logistic regression. OR (odds ratio) states how many times the odds of recurrence change when a numerical predictor increases by one unit or a binary predictor changes from 0 to 1. For _per7 variables, the increase is seven treatment days; for log2-transformed variables, it is a doubling of the original value. For other categorical predictors, OR describes the change from the reference category to the category shown in the row. n is the number of patients analysed; lower and upper are the 95% profile-likelihood confidence limits"
)
```

## Recurrence within 90 days

Show the unadjusted associations.

```{r}
unadjusted_90D <- unadjusted_table(
  "recurence_till_90D",
  unadjusted_predictors,
  data_analysis
)
kableExtra::kable(
  unadjusted_90D,
  digits = 3,
  caption = "Unadjusted associations with recurrence within 90 days after therapy completion. Each predictor was fitted separately using logistic regression. OR (odds ratio) states how many times the odds of recurrence change when a numerical predictor increases by one unit or a binary predictor changes from 0 to 1. For _per7 variables, the increase is seven treatment days; for log2-transformed variables, it is a doubling of the original value. For other categorical predictors, OR describes the change from the reference category to the category shown in the row. n is the number of patients analysed; lower and upper are the 95% profile-likelihood confidence limits"
)
```

# Multivariable regression

## 30-day recurrence. Sensitivity ATB duration per additional seven days

Fit the model

```{r}
m_30D_effective_7d <- glm(
  recurence_till_1M ~
    ATB_sensitivity_per7 +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10),
  data = data_analysis,
  family = binomial(link = "logit")
)
summary(m_30D_effective_7d)
car::vif(m_30D_effective_7d)

sjPlot::tab_model(
  m_30D_effective_7d,
  pred.labels = unname(
    my_labels_dict[names(coef(m_30D_effective_7d))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "30-day recurrence. Sensitivity ATB duration per additional seven days: adjusted odds ratios"
)

```

Plot the model

```{r, fig.height=6.0, fig.width=5.4}
#| fig-cap: "Figure 3. 30-day recurrence. Sensitivity ATB duration per additional seven days. Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. OR states how many times recurrence odds change when a numerical predictor increases by one modelled unit or a binary predictor changes from 0 to 1. For other categorical predictors, the change is from the reference category to the category shown. The dashed line marks OR = 1. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury"

myplot <- plot_my_model(
  m_30D_effective_7d, 
  axis.lim = c(0.5, 4)
  )

plotac <- "fig_x03"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```

## 90-day recurrence. Sensitivity ATB duration per additional seven days

Fit the model

```{r}
m_90D_effective_7d <- glm(
  recurence_till_90D ~
    ATB_sensitivity_per7 +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10),
  data = data_analysis,
  family = binomial(link = "logit")
)
summary(m_90D_effective_7d)
car::vif(m_90D_effective_7d)

sjPlot::tab_model(
  m_90D_effective_7d,
  pred.labels = unname(
    my_labels_dict[names(coef(m_90D_effective_7d))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "90-day recurrence. Sensitivity ATB duration per additional seven days: adjusted odds ratios"
)

```

Plot the model

```{r, fig.height=6.0, fig.width=5.4}
#| fig-cap: "Figure 4. 90-day recurrence. Sensitivity ATB duration per additional seven days. Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. OR states how many times recurrence odds change when a numerical predictor increases by one modelled unit or a binary predictor changes from 0 to 1. For other categorical predictors, the change is from the reference category to the category shown. The dashed line marks OR = 1. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury"

myplot <- plot_my_model(
  m_90D_effective_7d, 
  axis.lim = c(0.49, 5)
  )

plotac <- "fig_x04"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```

## 30-day recurrence. Sensitivity ATB duration per doubling

Fit the model

```{r}
m_30D_effective_log2 <- glm(
  recurence_till_1M ~
    log2_ATB_sensitivity_duration +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10),
  data = data_analysis,
  family = binomial(link = "logit")
)
summary(m_30D_effective_log2)
car::vif(m_30D_effective_log2)

sjPlot::tab_model(
  m_30D_effective_log2,
  pred.labels = unname(
    my_labels_dict[names(coef(m_30D_effective_log2))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "30-day recurrence. Sensitivity ATB duration per doubling: adjusted odds ratios"
)

```

Plot the model

```{r, fig.height=6.0, fig.width=5.4}
#| fig-cap: "Figure 5. 30-day recurrence. Sensitivity ATB duration per doubling. Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. OR states how many times recurrence odds change when a numerical predictor increases by one modelled unit or a binary predictor changes from 0 to 1. For other categorical predictors, the change is from the reference category to the category shown. The dashed line marks OR = 1. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury"

myplot <- plot_my_model(
  m_30D_effective_log2, 
  axis.lim = c(0.49, 4)
  )


plotac <- "fig_x05"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```

## 90-day recurrence. Sensitivity ATB duration per doubling

Fit the model

```{r}
m_90D_effective_log2 <- glm(
  recurence_till_90D ~
    log2_ATB_sensitivity_duration +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10),
  data = data_analysis,
  family = binomial(link = "logit")
)
summary(m_90D_effective_log2)
car::vif(m_90D_effective_log2)

sjPlot::tab_model(
  m_90D_effective_log2,
  pred.labels = unname(
    my_labels_dict[names(coef(m_90D_effective_log2))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "90-day recurrence. Sensitivity ATB duration per doubling: adjusted odds ratios"
)

```
Plot the model

```{r, fig.height=6.0, fig.width=5.4}
#| fig-cap: "Figure 6. 90-day recurrence. Sensitivity ATB duration per doubling. Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. OR states how many times recurrence odds change when a numerical predictor increases by one modelled unit or a binary predictor changes from 0 to 1. For other categorical predictors, the change is from the reference category to the category shown. The dashed line marks OR = 1. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury"

myplot <- plot_my_model(
  m_90D_effective_log2,
  axis.lim = c(0.49, 5.2))


plotac <- "fig_x06"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```

## 30-day recurrence. Sensitivity ATB duration: <=13 versus >13 days

Fit the model

```{r}
m_30D_effective_short <- glm(
  recurence_till_1M ~
    treatment_under14D +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10),
  data = data_analysis,
  family = binomial(link = "logit")
)
summary(m_30D_effective_short)
car::vif(m_30D_effective_short)

sjPlot::tab_model(
  m_30D_effective_short,
  pred.labels = unname(
    my_labels_dict[names(coef(m_30D_effective_short))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "30-day recurrence. Sensitivity ATB duration: <=13 versus >13 days: adjusted odds ratios"
)

```
Plot the model

```{r, fig.height=6.0, fig.width=5.4}
#| fig-cap: "Figure 7. 30-day recurrence. Sensitivity ATB duration: <=13 versus >13 days. Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. OR states how many times recurrence odds change when a numerical predictor increases by one modelled unit or a binary predictor changes from 0 to 1. For other categorical predictors, the change is from the reference category to the category shown. The dashed line marks OR = 1. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury"

myplot <- plot_my_model(
  m_30D_effective_short, 
  axis.lim = c(0.49, 4.9)
  )


plotac <- "fig_x07"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```

## 90-day recurrence. Sensitivity ATB duration: <=13 versus >13 days

Fit the model

```{r}
m_90D_effective_short <- glm(
  recurence_till_90D ~
    treatment_under14D +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10),
  data = data_analysis,
  family = binomial(link = "logit")
)
summary(m_90D_effective_short)
car::vif(m_90D_effective_short)

sjPlot::tab_model(
  m_90D_effective_short,
  pred.labels = unname(
    my_labels_dict[names(coef(m_90D_effective_short))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "90-day recurrence. Sensitivity ATB duration: <=13 versus >13 days: adjusted odds ratios"
)

```

Plot the model

```{r, fig.height=6.0, fig.width=5.4}
#| fig-cap: "Figure 8. 90-day recurrence. Sensitivity ATB duration: <=13 versus >13 days. Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. OR states how many times recurrence odds change when a numerical predictor increases by one modelled unit or a binary predictor changes from 0 to 1. For other categorical predictors, the change is from the reference category to the category shown. The dashed line marks OR = 1. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury"

myplot <- plot_my_model(
  m_90D_effective_short, 
  axis.lim = c(0.44, 5)
  )


plotac <- "fig_x08"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```


## 30-day recurrence. Overall duration per seven days

Fit the model

```{r}
m_30D_overall_7d <- glm(
  recurence_till_1M ~
    ATB_overall_per7 +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10),
  data = data_analysis,
  family = binomial(link = "logit")
)
summary(m_30D_overall_7d)
car::vif(m_30D_overall_7d)

sjPlot::tab_model(
  m_30D_overall_7d,
  pred.labels = unname(
    my_labels_dict[names(coef(m_30D_overall_7d))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "30-day recurrence. Overall duration per seven days: adjusted odds ratios"
)

```

Plot the model

```{r, fig.height=6.0, fig.width=5.4}
#| fig-cap: "Figure 9. 30-day recurrence. Overall duration per seven days. Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. OR states how many times recurrence odds change when a numerical predictor increases by one modelled unit or a binary predictor changes from 0 to 1. For other categorical predictors, the change is from the reference category to the category shown. The dashed line marks OR = 1. Overall duration includes all antibiotic treatment irrespective of in vitro susceptibility. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury"

myplot <- plot_my_model(
  m_30D_overall_7d, 
  axis.lim = c(0.49, 4.9)
  )


plotac <- "fig_x09"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```


## 90-day recurrence. Overall duration per seven days

Fit the model

```{r}

m_90D_overall_7d <- glm(
  recurence_till_90D ~
    ATB_overall_per7 +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10),
  data = data_analysis,
  family = binomial(link = "logit")
)
summary(m_90D_overall_7d)
car::vif(m_90D_overall_7d)

sjPlot::tab_model(
  m_90D_overall_7d,
  pred.labels = unname(
    my_labels_dict[names(coef(m_90D_overall_7d))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "90-day recurrence. Overall duration per seven days: adjusted odds ratios"
)

```

Plot the model

```{r, fig.height=6.0, fig.width=5.4}
#| fig-cap: "Figure 10. 90-day recurrence. Overall duration per seven days. Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. OR states how many times recurrence odds change when a numerical predictor increases by one modelled unit or a binary predictor changes from 0 to 1. For other categorical predictors, the change is from the reference category to the category shown. The dashed line marks OR = 1. Overall duration includes all antibiotic treatment irrespective of in vitro susceptibility. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury"

myplot <- plot_my_model(
  m_90D_overall_7d,
  axis.lim = c(0.24, 5)
  )


plotac <- "fig_x10"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```

## 30-day recurrence. Overall duration per doubling

Fit the model

```{r}
m_30D_overall_log2 <- glm(
  recurence_till_1M ~
    log2_ATB_duration_overall +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10),
  data = data_analysis,
  family = binomial(link = "logit")
)
summary(m_30D_overall_log2)
car::vif(m_30D_overall_log2)

sjPlot::tab_model(
  m_30D_overall_log2,
  pred.labels = unname(
    my_labels_dict[names(coef(m_30D_overall_log2))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "30-day recurrence. Overall duration per doubling: adjusted odds ratios"
)

```

Plot the model

```{r, fig.height=6.0, fig.width=5.4}

#| fig-cap: "Figure 11. 30-day recurrence. Overall duration per doubling. Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. OR states how many times recurrence odds change when a numerical predictor increases by one modelled unit or a binary predictor changes from 0 to 1. For other categorical predictors, the change is from the reference category to the category shown. The dashed line marks OR = 1. Overall duration includes all antibiotic treatment irrespective of in vitro susceptibility. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury"

myplot <- plot_my_model(
  m_30D_overall_log2,
  axis.lim = c(0.49, 4.5)
  )

plotac <- "fig_x11"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```

## 90-day recurrence. Overall duration per doubling

Fit the model

```{r}
m_90D_overall_log2 <- glm(
  recurence_till_90D ~
    log2_ATB_duration_overall +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10),
  data = data_analysis,
  family = binomial(link = "logit")
)
summary(m_90D_overall_log2)
car::vif(m_90D_overall_log2)

sjPlot::tab_model(
  m_90D_overall_log2,
  pred.labels = unname(
    my_labels_dict[names(coef(m_90D_overall_log2))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "90-day recurrence. Overall duration per doubling: adjusted odds ratios"
)

```

Plot the model

```{r, fig.height=6.0, fig.width=5.4}
#| fig-cap: "Figure 12. 90-day recurrence. Overall duration per doubling. Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. OR states how many times recurrence odds change when a numerical predictor increases by one modelled unit or a binary predictor changes from 0 to 1. For other categorical predictors, the change is from the reference category to the category shown. The dashed line marks OR = 1. Overall duration includes all antibiotic treatment irrespective of in vitro susceptibility. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury"

myplot <- plot_my_model(
  m_90D_overall_log2, 
  axis.lim = c(0.49, 5)
  )

plotac <- "fig_x12"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```

## 30-day recurrence. Sensitivity ATB duration with immunosuppression

Add maintenance immunosuppression and prior depletion or rejection treatment to the corresponding original model. The original covariates, remain unchanged.

```{r}
m_30D_sensitivity_IS <- glm(
  recurence_till_1M ~
    ATB_sensitivity_per7 +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10) +
    immunosuppression_regimen +
    depletion_induction_or_rejection_treatment_6M,
  data = data_analysis,
  family = binomial(link = "logit")
)
summary(m_30D_sensitivity_IS)
car::vif(m_30D_sensitivity_IS)
sjPlot::tab_model(
  m_30D_sensitivity_IS,
  pred.labels = unname(
    my_labels_dict[names(coef(m_30D_sensitivity_IS))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "30-day recurrence. Sensitivity ATB duration with immunosuppression: adjusted odds ratios"
)
```

Plot the model

```{r, fig.height=6.0, fig.width=5.4}
#| fig-cap: "Figure 13. 30-day recurrence. Sensitivity ATB duration with immunosuppression. Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. The model retains the original adjustment set and adds maintenance immunosuppression and depletion or rejection treatment in the preceding six months. OR states how many times recurrence odds change per modelled numerical unit, from 0 to 1 for binary predictors, or from the reference category to the category shown. Sensitivity ATB duration is per seven days, age per 30 years, calendar time per ten years and log2 variables per doubling. The dashed line marks OR = 1. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury. IS denotes maintenance immunosuppression, with standard triple therapy as reference; depletion/rejection treatment refers to the preceding six months"

myplot <- plot_my_model(
  m_30D_sensitivity_IS,
  axis.lim = c(0.49, 4.5)
  )


plotac <- "fig_x13"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```

## 90-day recurrence. Sensitivity ATB duration with immunosuppression

Add maintenance immunosuppression and prior depletion or rejection treatment to the corresponding original model. The original covariates, remain unchanged.

```{r}
m_90D_sensitivity_IS <- glm(
  recurence_till_90D ~
    ATB_sensitivity_per7 +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10) +
    immunosuppression_regimen +
    depletion_induction_or_rejection_treatment_6M,
  data = data_analysis,
  family = binomial(link = "logit")
)
summary(m_90D_sensitivity_IS)
car::vif(m_90D_sensitivity_IS)
sjPlot::tab_model(
  m_90D_sensitivity_IS,
  pred.labels = unname(
    my_labels_dict[names(coef(m_90D_sensitivity_IS))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "90-day recurrence. Sensitivity ATB duration with immunosuppression: adjusted odds ratios"
)
```

Plot the model

```{r, fig.height=6.0, fig.width=5.4}
#| fig-cap: "Figure 14. 90-day recurrence. Sensitivity ATB duration with immunosuppression. Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. The model retains the original adjustment set and adds maintenance immunosuppression and depletion or rejection treatment in the preceding six months. OR states how many times recurrence odds change per modelled numerical unit, from 0 to 1 for binary predictors, or from the reference category to the category shown. Sensitivity ATB duration is per seven days, age per 30 years, calendar time per ten years and log2 variables per doubling. The dashed line marks OR = 1. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury. IS denotes maintenance immunosuppression, with standard triple therapy as reference; depletion/rejection treatment refers to the preceding six months"

myplot <- plot_my_model(
  m_90D_sensitivity_IS, 
  axis.lim = c(0.49, 5)
  )


plotac <- "fig_x14"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```


## 90-day, sensitivity per 7D, data 2017+ only

Fit the model

```{r}
m_90D_effective_7d_2017 <- glm(
  recurence_till_90D ~
    ATB_sensitivity_per7 +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10),
  data = data_analysis |> 
    filter(calendar_year >= 2017),
  family = binomial(link = "logit")
)
summary(m_90D_effective_7d_2017)
car::vif(m_90D_effective_7d_2017)

sjPlot::tab_model(
  m_90D_effective_7d_2017,
  pred.labels = unname(
    my_labels_dict[names(coef(m_90D_effective_7d_2017))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "90-day recurrence. Sensitivity ATB duration per additional seven days: adjusted odds ratios"
)

```

Plot the model

```{r, fig.height=6.0, fig.width=5.4}
#| fig-cap: "Figure 15. 90-day recurrence. Sensitivity ATB duration per additional seven days (year 2017+). Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. OR states how many times recurrence odds change when a numerical predictor increases by one modelled unit or a binary predictor changes from 0 to 1. For other categorical predictors, the change is from the reference category to the category shown. The dashed line marks OR = 1. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury"

myplot <- plot_my_model(
  m_90D_effective_7d_2017, 
  axis.lim = c(0.49, 5)
  )


plotac <- "fig_x15"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```

## 30-day, sensitivy per 7D, data 2017+ only

Fit the model

```{r}
m_30D_effective_7d_2017 <- glm(
  recurence_till_1M ~
    ATB_sensitivity_per7 +
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    I(years_from2019 / 10),
  data = data_analysis |> filter(calendar_year >= 2017),
  family = binomial(link = "logit")
)
summary(m_30D_effective_7d_2017)
car::vif(m_30D_effective_7d_2017)

sjPlot::tab_model(
  m_30D_effective_7d_2017,
  pred.labels = unname(
    my_labels_dict[names(coef(m_30D_effective_7d_2017))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "30-day recurrence. Sensitivity ATB duration per additional seven days: adjusted odds ratios"
)

```
Plot the model

```{r, fig.height=6.0, fig.width=5.4}
#| fig-cap: "Figure 16. 30-day recurrence. Sensitivity ATB duration per additional seven days (year 2017+). Points show adjusted logistic-regression odds ratios and horizontal lines show 95% profile-likelihood confidence intervals. OR states how many times recurrence odds change when a numerical predictor increases by one modelled unit or a binary predictor changes from 0 to 1. For other categorical predictors, the change is from the reference category to the category shown. The dashed line marks OR = 1. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury"

myplot <- plot_my_model(
  m_30D_effective_7d_2017, 
  axis.lim = c(0.49, 4.5)
  )


plotac <- "fig_x16"
myplot <- save_plot(myplot, plotac, width = 5.4, height = 6.0)
myplot
```


# Matching

Match treatment groups 1:1 within calendar periods

```{r}
matching_data <- data_analysis

match_model <- MatchIt::matchit(
  treatment_under14D ~
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    stent_in_situ +
    bph_pca_subvesical_obstruction +
    urethral_stricture +
    renofunctional_obstruction +
    diabetes_severe +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    years_from2019 +
    CRP_entry_by100,
  data = matching_data,
  method = "nearest",
  distance = "glm",
  link = "linear.logit",
  exact = ~ calendar_period,
  caliper = 0.2,
  std.caliper = TRUE,
  ratio = 1,
  replace = FALSE,
  estimand = "ATT"
)

match_summary <- summary(match_model, standardize = TRUE)
matched_data <- MatchIt::match_data(match_model) |>
  data.frame()
```

The 2017+ subset retains complete pairs from all-years matching

Create the 2017+ subsets and show sample sizes.

```{r}
matching_data_2017 <- matching_data |>
  dplyr::filter(calendar_year >= 2017) |>
  data.frame()

matched_data_2017 <- matched_data |>
  dplyr::filter(calendar_year >= 2017) |>
  data.frame()

matching_counts <- data.frame(
  cohort = c("All", "2017+"),
  available = c(nrow(matching_data), nrow(matching_data_2017)),
  matched = c(nrow(matched_data), nrow(matched_data_2017)),
  pairs = c(
    dplyr::n_distinct(matched_data$subclass),
    dplyr::n_distinct(matched_data_2017$subclass)
  )
)

kableExtra::kable(
  matching_counts,
  caption = "Matching sample sizes for all years and 2017+. available counts eligible patients before matching; matched counts retained patients; pairs counts matched pairs. The 2017+ subset is selected after matching across all years and retains the original pairs and weights"
)
```

## Exploration, all

### Safety outcomes

See the Safety outcomes chapter for infections and readmissions within 30 and 90 days after therapy completion

### Observed treatment duration after matching

Describe actual sensitivity ATB duration, which defines the treatment groups, and overall ATB duration in the same matched patients.

```{r}
matched_duration_all <- matched_data |>
  dplyr::select(
    treatment_group,
    ATB_sensitivity_duration,
    ATB_duration_overall
  ) |>
  tidyr::pivot_longer(
    cols = c(
      ATB_sensitivity_duration,
      ATB_duration_overall
    ),
    names_to = "duration",
    values_to = "days"
  ) |>
  dplyr::group_by(
    treatment_group,
    duration
  ) |>
  dplyr::summarise(
    patients = dplyr::n(),
    available = sum(!is.na(days)),
    median_days = median(days, na.rm = TRUE),
    q25_days = quantile(days, 0.25, na.rm = TRUE),
    q75_days = quantile(days, 0.75, na.rm = TRUE),
    min_days = min(days, na.rm = TRUE),
    max_days = max(days, na.rm = TRUE),
    .groups = "drop"
  ) |>
  data.frame()

kableExtra::kable(
  matched_duration_all,
  digits = 1,
  caption = "All years. Observed antibiotic treatment duration in the matched cohort. treatment_group is defined by sensitivity ATB duration: short <=13 days and long >13 days. ATB_sensitivity_duration is the interval from sensitivity ATB initiation to therapy completion; ATB_duration_overall is the interval from overall ATB initiation to completion. patients is the group size; available counts nonmissing durations; median_days is the median; q25_days and q75_days are the lower and upper quartiles; min_days and max_days give the observed range. All durations are in days"
)
```

### Balance, all

Check balance

```{r, fig.height=6.7, fig.width=6.1}
#| fig-cap: "Figure 17. All years. Covariate balance before and after matching. Points show absolute standardized mean differences, standardized by the pre-matching short-treatment group in the displayed cohort; colours distinguish before and after matching. The dashed line marks 0.1. Original all-years matching weights are retained; no rematching is performed. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury. Obstruction risk factors is the umbrella category; subvesical obstruction includes urethral stricture. Ureteral stent denotes a stent in situ at discharge"

matching_balance_all <- summary(
  match_model,
  standardize = TRUE
)

matching_before_all <- as.data.frame(
  matching_balance_all$sum.all,
  check.names = FALSE
) |>
  tibble::rownames_to_column("covariate") |>
  janitor::clean_names() |>
  dplyr::mutate(stage = "Before matching") |>
  data.frame()

matching_after_all <- as.data.frame(
  matching_balance_all$sum.matched,
  check.names = FALSE
) |>
  tibble::rownames_to_column("covariate") |>
  janitor::clean_names() |>
  dplyr::mutate(stage = "After matching") |>
  data.frame()

matching_balance_plot_all <- dplyr::bind_rows(
  matching_before_all,
  matching_after_all
) |>
  data.frame()

myplot <- ggplot(
  matching_balance_plot_all,
  aes(abs(std_mean_diff), covariate, colour = stage)
) +
  geom_vline(xintercept = 0.1, linetype = "dashed", colour = "grey50") +
  geom_point() +
  scale_y_discrete(labels = function(x) {
    dplyr::coalesce(unname(plot_labels_dict[x]), x)
  }) +
  scale_colour_manual(values = c("#A65F35", "#477DA0")) +
  labs(x = "Absolute standardized mean difference", y = NULL,
       colour = NULL)

plotac <- "fig_x17_matching"

myplot <- save_plot(myplot, plotac, width = 6.1, height = 6.7)
myplot
```

## KM after matching, all

Estimate recurrence-free survival and compare matched groups

The existing recurrence indicators are retained. Empty confirmed-recurrence dates mean no recurrence within the recorded 90-day window, as agreed. Patients without recurrence in this window are administratively censored at day 90. The fixed-day comparisons assume recurrence status is known through day 90 for all matched patients; there is no earlier loss to follow-up in this coding.

### Survival curves and overall log-rank test

Create the survival data and test the curves over the full 90 days. subclass identifies the matched pair.

```{r}
matched_survival_all <- matched_data |>
  dplyr::mutate(
    treatment = factor(
      dplyr::if_else(treatment_under14D == 1, "short", "long"),
      levels = c("long", "short")
    ),
    time_90D = dplyr::if_else(
      recurence_till_90D == 1,
      as.numeric(Infection_to90D_day - EndDate_therapy),
      90
    )
  ) |>
  data.frame()

km_matched_90D_all <- survfit(
  Surv(time_90D, recurence_till_90D) ~ treatment,
  data = matched_survival_all,
  conf.type = "log-log"
)

logrank_matched_90D_all <- survdiff(
  Surv(time_90D, recurence_till_90D) ~
    treatment + strata(subclass),
  data = matched_survival_all,
  rho = 0
)

logrank_p_all <- pchisq(
  logrank_matched_90D_all$chisq,
  df = 1,
  lower.tail = FALSE
)

logrank_results_all <- data.frame(
  pairs = dplyr::n_distinct(matched_survival_all$subclass),
  patients = nrow(matched_survival_all),
  chi_squared = logrank_matched_90D_all$chisq,
  df = 1,
  p_value = logrank_p_all
)
kableExtra::kable(
  logrank_results_all,
  digits = 3,
  caption = "All years. Overall comparison of recurrence-free survival through 90 days after therapy completion in the 1:1 matched cohort. The log-rank test is stratified by matched pair. pairs and patients are the numbers analysed; chi_squared is the test statistic, df its degrees of freedom, and p_value the unadjusted overall p-value"
)
```

### Post-hoc comparisons at days 30 and 90

```{r}
matched_pairs_all <- matched_survival_all |>
  dplyr::select(
    subclass,
    treatment,
    recurence_till_1M,
    recurence_till_90D
  ) |>
  tidyr::pivot_longer(
    cols = c(recurence_till_1M, recurence_till_90D),
    names_to = "outcome",
    values_to = "event"
  ) |>
  dplyr::mutate(
    day = dplyr::if_else(outcome == "recurence_till_1M", 30, 90)
  ) |>
  dplyr::select(-outcome) |>
  tidyr::pivot_wider(
    names_from = treatment,
    values_from = event
  ) |>
  data.frame()

matched_posthoc_all <- matched_pairs_all |>
  dplyr::group_by(day) |>
  dplyr::summarise(
    pairs = dplyr::n(),
    short_events = sum(short),
    long_events = sum(long),
    short_only = sum(short == 1 & long == 0),
    long_only = sum(short == 0 & long == 1),
    .groups = "drop"
  ) |>
  dplyr::rowwise() |>
  dplyr::mutate(
    p_value = if (short_only + long_only == 0) {
      1
    } else {
      binom.test(
        short_only,
        short_only + long_only,
        p = 0.5,
        alternative = "two.sided"
      )$p.value
    }
  ) |>
  dplyr::ungroup() |>
  dplyr::mutate(
    short_risk = short_events / pairs,
    long_risk = long_events / pairs,
    risk_difference = short_risk - long_risk,
    p_holm = p.adjust(p_value, method = "holm")
  ) |>
  dplyr::arrange(day) |>
  data.frame()

kableExtra::kable(
  matched_posthoc_all,
  digits = 3,
  caption = "All years. Post-hoc comparisons of recurrence by days 30 and 90 after therapy completion. short denotes sensitivity ATB duration <=13 days and long denotes >13 days. pairs is the number of matched pairs; short_events and long_events count patients with recurrence in each group. short_only and long_only count discordant pairs in which recurrence occurred only in the short-treatment or only in the long-treatment patient. short_risk and long_risk are recurrence proportions; risk_difference is short minus long. p_value is the two-sided exact McNemar p-value, calculated by a binomial test of discordant pairs; p_holm adjusts the two post-hoc p-values using Holm's method"
)
```

### Plot the matched survival curves

Show the overall pair-stratified log-rank p-value and the two Holm-adjusted post-hoc p-values. Shading represents pointwise confidence intervals for each curve.

```{r, fig.height=5.5, fig.width=6}
#| fig-cap: "Figure 18. All years. Recurrence-free survival through 90 days after therapy completion in the cohort matched 1:1 on propensity score. Curves are unadjusted Kaplan–Meier estimates for sensitivity ATB duration <=13 and >13 days; shading shows pointwise 95% confidence intervals calculated using Greenwood variance and the log-log transformation. Tick marks indicate censoring and the lower panel shows patients at risk. Vertical dashed lines mark days 30 and 90. The overall p-value is from a log-rank test stratified by matched pair; post-hoc p-values compare recurrence proportions by days 30 and 90 using two-sided exact McNemar tests with Holm adjustment across these two comparisons. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro"

km_p_text_all <- paste0(
  "Pair-stratified log-rank p = ",
  format.pval(logrank_p_all, digits = 3, eps = 0),
  "\nDay 30, post-hoc p (Holm) = ",
  format.pval(
    matched_posthoc_all$p_holm[matched_posthoc_all$day == 30],
    digits = 3,
    eps = 0
  ),
  "\nDay 90, post-hoc p (Holm) = ",
  format.pval(
    matched_posthoc_all$p_holm[matched_posthoc_all$day == 90],
    digits = 3,
    eps = 0
  )
)

myplot <- survminer::ggsurvplot(
  km_matched_90D_all,
  data = matched_survival_all,
  pval = km_p_text_all,
  pval.coord = c(40, 0.15),
  pval.size = 3.7,
  conf.int = TRUE,
  risk.table = TRUE,
  risk.table.y.text.col = FALSE,
  risk.table.fontsize = 3.6,
  censor.shape = 124,
  censor.size = 2,
  palette = c("#477DA0", "#A65F35"),
  xlab = "Days from the end of therapy",
  ylab = "Probability of remaining recurrence-free",
  legend.title = "Therapy duration",
  legend.labs = c(">13 days", "<=13 days"),
  break.time.by = 15,
  xlim = c(0, 90),
  ggtheme = theme_grey()
)

myplot$plot <- myplot$plot +
  geom_vline(
    xintercept = c(30, 90),
    linetype = "dashed",
    colour = "grey50"
  )

myplot$plot <- myplot$plot +
  theme(
    plot.title = element_text(size = 12),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11)
  )

myplot$table <- myplot$table +
  theme(
    plot.title = element_text(size = 10),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11)
  )

myplot <- cowplot::plot_grid(
  myplot$plot,
  myplot$table + theme(legend.position = "none"),
  ncol = 1,
  rel_heights = c(0.75, 0.25),
  align = "v",
  axis = "lr"
)



plotac <- "fig_x18_KM"
myplot <- save_plot(myplot, plotac, width = 6, height = 5.5)
myplot
```

### HR, 90D

```{r}
m_cox_matched_90D_all <- coxph(
  Surv(time_90D, recurence_till_90D) ~ treatment_under14D,
  data = matched_survival_all,
  cluster = subclass
)

cox_summary_all <- summary(m_cox_matched_90D_all)

cox_results_all <- data.frame(
  comparison = "<=13 versus >13 days",
  n = m_cox_matched_90D_all$n,
  events = m_cox_matched_90D_all$nevent,
  HR = cox_summary_all$conf.int[, "exp(coef)"],
  lower = cox_summary_all$conf.int[, "lower .95"],
  upper = cox_summary_all$conf.int[, "upper .95"],
  p_value = cox_summary_all$coefficients[, "Pr(>|z|)"],
  row.names = NULL
)

kableExtra::kable(
  cox_results_all,
  digits = 3,
  caption = "All years. Recurrence within 90 days after therapy completion in the matched cohort. A Cox proportional hazards model included treatment group as the sole predictor, with robust variance clustered by matched pair. HR compares sensitivity ATB treatment lasting <=13 days with >13 days; HR >1 indicates a higher recurrence hazard with shorter treatment. n is the number of patients; events is the number of recurrences; lower and upper are robust Wald 95% confidence limits; p_value is the two-sided robust Wald p-value"
)
```

### HR, 30D

Estimate the treatment-group hazard ratio over the first 30 days after therapy completion in the original matched cohort. Follow-up is administratively censored at day 30; recurrences occurring later are not counted as events in this analysis.

```{r}
matched_survival_30D_all <- matched_survival_all |>
  dplyr::mutate(
    time_30D = pmin(time_90D, 30),
    event_30D = as.integer(
      recurence_till_90D == 1 & time_90D <= 30
    )
  ) |>
  data.frame()

m_cox_matched_30D_all <- coxph(
  Surv(time_30D, event_30D) ~ treatment_under14D,
  data = matched_survival_30D_all,
  cluster = subclass
)

cox_summary_30D_all <- summary(m_cox_matched_30D_all)

cox_results_30D_all <- data.frame(
  comparison = "<=13 versus >13 days",
  n = m_cox_matched_30D_all$n,
  events = m_cox_matched_30D_all$nevent,
  HR = cox_summary_30D_all$conf.int[, "exp(coef)"],
  lower = cox_summary_30D_all$conf.int[, "lower .95"],
  upper = cox_summary_30D_all$conf.int[, "upper .95"],
  p_value = cox_summary_30D_all$coefficients[, "Pr(>|z|)"],
  row.names = NULL
)

kableExtra::kable(
  cox_results_30D_all,
  digits = 3,
  caption = "All years. Recurrence within 30 days after therapy completion in the original matched cohort, irrespective of pathogen concordance. Follow-up was administratively censored at day 30. A Cox proportional hazards model included treatment group as the sole predictor, with robust variance clustered by matched pair. HR states how many times the recurrence hazard changes from >13 to <=13 days of sensitivity ATB treatment; HR >1 indicates a higher hazard with shorter treatment. n is the number analysed; events counts recurrences; lower and upper are robust Wald 95% confidence limits; p_value is the two-sided robust Wald p-value"
)
```

## Exploration, 2017+

### Safety outcomes

See the Safety outcomes chapter for infections and readmissions within 30 and 90 days after therapy completion

### Observed treatment duration after matching

Describe actual sensitivity ATB duration, which defines the treatment groups, and overall ATB duration in the same matched patients.

```{r}
matched_duration_2017 <- matched_data_2017 |>
  dplyr::select(
    treatment_group,
    ATB_sensitivity_duration,
    ATB_duration_overall
  ) |>
  tidyr::pivot_longer(
    cols = c(
      ATB_sensitivity_duration,
      ATB_duration_overall
    ),
    names_to = "duration",
    values_to = "days"
  ) |>
  dplyr::group_by(
    treatment_group,
    duration
  ) |>
  dplyr::summarise(
    patients = dplyr::n(),
    available = sum(!is.na(days)),
    median_days = median(days, na.rm = TRUE),
    q25_days = quantile(days, 0.25, na.rm = TRUE),
    q75_days = quantile(days, 0.75, na.rm = TRUE),
    min_days = min(days, na.rm = TRUE),
    max_days = max(days, na.rm = TRUE),
    .groups = "drop"
  ) |>
  data.frame()

kableExtra::kable(
  matched_duration_2017,
  digits = 1,
  caption = "2017+. Observed antibiotic treatment duration in the matched cohort. treatment_group is defined by sensitivity ATB duration: short <=13 days and long >13 days. ATB_sensitivity_duration is the interval from sensitivity ATB initiation to therapy completion; ATB_duration_overall is the interval from overall ATB initiation to completion. patients is the group size; available counts nonmissing durations; median_days is the median; q25_days and q75_days are the lower and upper quartiles; min_days and max_days give the observed range. All durations are in days"
)
```

### Balance, 2017+

Check balance

```{r, fig.height=6.7, fig.width=6.1}
#| fig-cap: "Figure 19. 2017+. Covariate balance before and after matching. Points show absolute standardized mean differences, standardized by the pre-matching short-treatment group in the displayed cohort; colours distinguish before and after matching. The dashed line marks 0.1. Original all-years matching weights are retained; no rematching is performed. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury. Obstruction risk factors is the umbrella category; subvesical obstruction includes urethral stricture. Ureteral stent denotes a stent in situ at discharge"

matching_keep_2017 <- matching_data$calendar_year >= 2017
match_model_balance_2017 <- match_model
match_model_balance_2017$X <- match_model$X[
  matching_keep_2017, , drop = FALSE
]
match_model_balance_2017$treat <- match_model$treat[
  matching_keep_2017
]
match_model_balance_2017$weights <- match_model$weights[
  matching_keep_2017
]
match_model_balance_2017$distance <- match_model$distance[
  matching_keep_2017
]
match_model_balance_2017$discarded <- match_model$discarded[
  matching_keep_2017
]
match_model_balance_2017$subclass <- match_model$subclass[
  matching_keep_2017
]
match_model_balance_2017$match.matrix <- match_model$match.matrix[
  rownames(match_model$match.matrix) %in%
    names(match_model_balance_2017$treat), , drop = FALSE
]

matching_balance_2017 <- summary(
  match_model_balance_2017,
  standardize = TRUE
)

matching_before_2017 <- as.data.frame(
  matching_balance_2017$sum.all,
  check.names = FALSE
) |>
  tibble::rownames_to_column("covariate") |>
  janitor::clean_names() |>
  dplyr::mutate(stage = "Before matching") |>
  data.frame()

matching_after_2017 <- as.data.frame(
  matching_balance_2017$sum.matched,
  check.names = FALSE
) |>
  tibble::rownames_to_column("covariate") |>
  janitor::clean_names() |>
  dplyr::mutate(stage = "After matching") |>
  data.frame()

matching_balance_plot_2017 <- dplyr::bind_rows(
  matching_before_2017,
  matching_after_2017
) |>
  data.frame()

myplot <- ggplot(
  matching_balance_plot_2017,
  aes(abs(std_mean_diff), covariate, colour = stage)
) +
  geom_vline(xintercept = 0.1, linetype = "dashed", colour = "grey50") +
  geom_point() +
  scale_y_discrete(labels = function(x) {
    dplyr::coalesce(unname(plot_labels_dict[x]), x)
  }) +
  scale_colour_manual(values = c("#A65F35", "#477DA0")) +
  labs(x = "Absolute standardized mean difference", y = NULL,
       colour = NULL)

plotac <- "fig_x19_balance"
myplot <- save_plot(myplot, plotac, width = 6.1, height = 6.7)
myplot
```

## KM after matching, 2017+

### Survival curves and overall log-rank test

```{r}
matched_survival_2017 <- matched_data_2017 |>
  dplyr::mutate(
    treatment = factor(
      dplyr::if_else(treatment_under14D == 1, "short", "long"),
      levels = c("long", "short")
    ),
    time_90D = dplyr::if_else(
      recurence_till_90D == 1,
      as.numeric(Infection_to90D_day - EndDate_therapy),
      90
    )
  ) |>
  data.frame()

km_matched_90D_2017 <- survfit(
  Surv(time_90D, recurence_till_90D) ~ treatment,
  data = matched_survival_2017,
  conf.type = "log-log"
)

logrank_matched_90D_2017 <- survdiff(
  Surv(time_90D, recurence_till_90D) ~
    treatment + strata(subclass),
  data = matched_survival_2017,
  rho = 0
)

logrank_p_2017 <- pchisq(
  logrank_matched_90D_2017$chisq,
  df = 1,
  lower.tail = FALSE
)

logrank_results_2017 <- data.frame(
  pairs = dplyr::n_distinct(matched_survival_2017$subclass),
  patients = nrow(matched_survival_2017),
  chi_squared = logrank_matched_90D_2017$chisq,
  df = 1,
  p_value = logrank_p_2017
)
kableExtra::kable(
  logrank_results_2017,
  digits = 3,
  caption = "2017+. Overall comparison of recurrence-free survival through 90 days after therapy completion in the 1:1 matched cohort. The log-rank test is stratified by matched pair. pairs and patients are the numbers analysed; chi_squared is the test statistic, df its degrees of freedom, and p_value the unadjusted overall p-value"
)
```

### Post-hoc comparisons at days 30 and 90

```{r}
matched_pairs_2017 <- matched_survival_2017 |>
  dplyr::select(
    subclass,
    treatment,
    recurence_till_1M,
    recurence_till_90D
  ) |>
  tidyr::pivot_longer(
    cols = c(recurence_till_1M, recurence_till_90D),
    names_to = "outcome",
    values_to = "event"
  ) |>
  dplyr::mutate(
    day = dplyr::if_else(outcome == "recurence_till_1M", 30, 90)
  ) |>
  dplyr::select(-outcome) |>
  tidyr::pivot_wider(
    names_from = treatment,
    values_from = event
  ) |>
  data.frame()

matched_posthoc_2017 <- matched_pairs_2017 |>
  dplyr::group_by(day) |>
  dplyr::summarise(
    pairs = dplyr::n(),
    short_events = sum(short),
    long_events = sum(long),
    short_only = sum(short == 1 & long == 0),
    long_only = sum(short == 0 & long == 1),
    .groups = "drop"
  ) |>
  dplyr::rowwise() |>
  dplyr::mutate(
    p_value = if (short_only + long_only == 0) {
      1
    } else {
      binom.test(
        short_only,
        short_only + long_only,
        p = 0.5,
        alternative = "two.sided"
      )$p.value
    }
  ) |>
  dplyr::ungroup() |>
  dplyr::mutate(
    short_risk = short_events / pairs,
    long_risk = long_events / pairs,
    risk_difference = short_risk - long_risk,
    p_holm = p.adjust(p_value, method = "holm")
  ) |>
  dplyr::arrange(day) |>
  data.frame()

kableExtra::kable(
  matched_posthoc_2017,
  digits = 3,
  caption = "2017+. Post-hoc comparisons of recurrence by days 30 and 90 after therapy completion. short denotes sensitivity ATB duration <=13 days and long denotes >13 days. pairs is the number of matched pairs; short_events and long_events count patients with recurrence in each group. short_only and long_only count discordant pairs in which recurrence occurred only in the short-treatment or only in the long-treatment patient. short_risk and long_risk are recurrence proportions; risk_difference is short minus long. p_value is the two-sided exact McNemar p-value, calculated by a binomial test of discordant pairs; p_holm adjusts the two post-hoc p-values using Holm's method"
)
```

### Plot the matched survival curves

```{r, fig.height=6, fig.width=5.5}
#| fig-cap: "Figure 20. 2017+. Recurrence-free survival through 90 days after therapy completion in the cohort matched 1:1 on propensity score. Curves are unadjusted Kaplan–Meier estimates for sensitivity ATB duration <=13 and >13 days; shading shows pointwise 95% confidence intervals calculated using Greenwood variance and the log-log transformation. Tick marks indicate censoring and the lower panel shows patients at risk. Vertical dashed lines mark days 30 and 90. The overall p-value is from a log-rank test stratified by matched pair; post-hoc p-values compare recurrence proportions by days 30 and 90 using two-sided exact McNemar tests with Holm adjustment across these two comparisons. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro"

km_p_text_2017 <- paste0(
  "Pair-stratified log-rank p = ",
  format.pval(logrank_p_2017, digits = 3, eps = 0),
  "\nDay 30, post-hoc p (Holm) = ",
  format.pval(
    matched_posthoc_2017$p_holm[matched_posthoc_2017$day == 30],
    digits = 3,
    eps = 0
  ),
  "\nDay 90, post-hoc p (Holm) = ",
  format.pval(
    matched_posthoc_2017$p_holm[matched_posthoc_2017$day == 90],
    digits = 3,
    eps = 0
  )
)

myplot <- survminer::ggsurvplot(
  km_matched_90D_2017,
  data = matched_survival_2017,
  pval = km_p_text_2017,
  pval.coord = c(40, 0.15),
  pval.size = 3.7,
  conf.int = TRUE,
  risk.table = TRUE,
  risk.table.y.text.col = FALSE,
  risk.table.fontsize = 3.6,
  censor.shape = 124,
  censor.size = 2,
  palette = c("#477DA0", "#A65F35"),
  xlab = "Days from the end of therapy",
  ylab = "Probability of remaining recurrence-free",
  legend.title = "Therapy duration",
  legend.labs = c(">13 days", "<=13 days"),
  break.time.by = 15,
  xlim = c(0, 90),
  ggtheme = theme_grey()
)

myplot$plot <- myplot$plot +
  theme(
    plot.title = element_text(size = 12),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11)
  )

myplot$table <- myplot$table +
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11)
  )

myplot$plot <- myplot$plot +
  geom_vline(
    xintercept = c(30, 90),
    linetype = "dashed",
    colour = "grey50"
  )

myplot <- cowplot::plot_grid(
  myplot$plot,
  myplot$table + theme(legend.position = "none"),
  ncol = 1,
  rel_heights = c(0.75, 0.25),
  align = "v",
  axis = "lr"
)

plotac <- "fig_x25_2017"
myplot <- save_plot(myplot, plotac, width = 6, height = 5.5)
myplot
```

### HR, 90D

```{r}
m_cox_matched_90D_2017 <- coxph(
  Surv(time_90D, recurence_till_90D) ~ treatment_under14D,
  data = matched_survival_2017,
  cluster = subclass
)

cox_summary_2017 <- summary(m_cox_matched_90D_2017)

cox_results_2017 <- data.frame(
  comparison = "<=13 versus >13 days",
  n = m_cox_matched_90D_2017$n,
  events = m_cox_matched_90D_2017$nevent,
  HR = cox_summary_2017$conf.int[, "exp(coef)"],
  lower = cox_summary_2017$conf.int[, "lower .95"],
  upper = cox_summary_2017$conf.int[, "upper .95"],
  p_value = cox_summary_2017$coefficients[, "Pr(>|z|)"],
  row.names = NULL
)

kableExtra::kable(
  cox_results_2017,
  digits = 3,
  caption = "2017+. Recurrence within 90 days after therapy completion in the matched cohort. A Cox proportional hazards model included treatment group as the sole predictor, with robust variance clustered by matched pair. HR compares sensitivity ATB treatment lasting <=13 days with >13 days; HR >1 indicates a higher recurrence hazard with shorter treatment. n is the number of patients; events is the number of recurrences; lower and upper are robust Wald 95% confidence limits; p_value is the two-sided robust Wald p-value"
)
```

### HR, 30D

Estimate the treatment-group hazard ratio over the first 30 days after therapy completion in the original matched cohort. Follow-up is administratively censored at day 30; recurrences occurring later are not counted as events in this analysis.

```{r}
matched_survival_30D_2017 <- matched_survival_2017 |>
  dplyr::mutate(
    time_30D = pmin(time_90D, 30),
    event_30D = as.integer(
      recurence_till_90D == 1 & time_90D <= 30
    )
  ) |>
  data.frame()

m_cox_matched_30D_2017 <- coxph(
  Surv(time_30D, event_30D) ~ treatment_under14D,
  data = matched_survival_30D_2017,
  cluster = subclass
)

cox_summary_30D_2017 <- summary(m_cox_matched_30D_2017)

cox_results_30D_2017 <- data.frame(
  comparison = "<=13 versus >13 days",
  n = m_cox_matched_30D_2017$n,
  events = m_cox_matched_30D_2017$nevent,
  HR = cox_summary_30D_2017$conf.int[, "exp(coef)"],
  lower = cox_summary_30D_2017$conf.int[, "lower .95"],
  upper = cox_summary_30D_2017$conf.int[, "upper .95"],
  p_value = cox_summary_30D_2017$coefficients[, "Pr(>|z|)"],
  row.names = NULL
)

kableExtra::kable(
  cox_results_30D_2017,
  digits = 3,
  caption = "2017+. Recurrence within 30 days after therapy completion in the original matched cohort, irrespective of pathogen concordance. Follow-up was administratively censored at day 30. A Cox proportional hazards model included treatment group as the sole predictor, with robust variance clustered by matched pair. HR states how many times the recurrence hazard changes from >13 to <=13 days of sensitivity ATB treatment; HR >1 indicates a higher hazard with shorter treatment. n is the number analysed; events counts recurrences; lower and upper are robust Wald 95% confidence limits; p_value is the two-sided robust Wald p-value"
)
```

## Relapse matching

Relapse is defined as recurrence within 30 days after therapy completion with concordant pathogens in the initial and recurrent infections. Following the clinician's definition, hemoculture_agreed is interpreted here as concordance between these two infections. The analysis includes patients with an identified pathogen in InfAgent_1.

### Define eligible cohort

Inspect the recorded initial pathogens and the entries excluded as unidentified. Normalization below affects only the eligibility check; the original pathogen column is retained.

```{r}
unidentified_agents <- c(
  "",
  "0",
  "nezachyceno",
  "nezachycen",
  "nezachycena",
  "nezjištěno",
  "nezjisteno",
  "negativní",
  "negativni",
  "neg",
  "neg.",
  "negativni kultivace"
)

relapse_data <- data_analysis |>
  dplyr::mutate(
    initial_agent_text = stringr::str_to_lower(
      stringr::str_squish(InfAgent_1)
    ),
    initial_agent_identified = !is.na(initial_agent_text) &
      !(initial_agent_text %in% unidentified_agents),
    relapse_30D = dplyr::case_when(
      recurence_till_1M == 0 ~ 0,
      recurence_till_1M == 1 & hemoculture_agreed == 1 ~ 1,
      recurence_till_1M == 1 & hemoculture_agreed == 0 ~ 0,
      TRUE ~ NA_real_
    )
  ) |>
  data.frame()

agent_check <- relapse_data |>
  dplyr::count(
    InfAgent_1,
    initial_agent_identified,
    name = "patients"
  ) |>
  data.frame()

kableExtra::kable(
  agent_check,
  caption = "Initial pathogen records and eligibility. InfAgent_1 is the original recorded value; initial_agent_identified indicates whether the entry is retained as an identified pathogen; patients is the number with that entry. Non-pathogen comments not covered by the explicit exclusion list require review"
)

relapse_data <- relapse_data |>
  dplyr::filter(initial_agent_identified) |>
  data.frame()

relapse_sample <- data.frame(
  available = nrow(data_analysis),
  excluded_initial_agent = nrow(data_analysis) - nrow(relapse_data),
  eligible = nrow(relapse_data),
  unknown_relapse = sum(is.na(relapse_data$relapse_30D))
)
```

### Repeat propensity-score matching

Match the identified-pathogen cohort across all years. Relapse status is not used to select matches. The supplied relapse propensity formula is retained unchanged: it includes diabetes and CRP_max_by100 in addition to the 16 covariates in the main matching formula. These two propensity specifications are intentionally not harmonized in this revision.

```{r}
match_relapse <- MatchIt::matchit(
  treatment_under14D ~
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    urology_acute +
    stent_in_situ +
    bph_pca_subvesical_obstruction +
    urethral_stricture +
    renofunctional_obstruction +
    diabetes_severe +
    diabetes +
    mra_positive +
    bad_response_early_worsening +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    years_from2019 +
    CRP_entry_by100 +
    CRP_max_by100,
  data = relapse_data,
  method = "nearest",
  distance = "glm",
  link = "linear.logit",
  exact = ~ calendar_period,
  caliper = 0.2,
  std.caliper = TRUE,
  ratio = 1,
  replace = FALSE,
  estimand = "ATT"
)

matched_relapse <- MatchIt::match_data(match_relapse) |>
  data.frame()

relapse_matching_counts <- data.frame(
  eligible = nrow(relapse_data),
  matched = nrow(matched_relapse),
  unmatched = nrow(relapse_data) - nrow(matched_relapse),
  pairs = dplyr::n_distinct(matched_relapse$subclass)
)

kableExtra::kable(
  relapse_matching_counts,
  caption = "Matching for the relapse analysis. eligible is the restricted cohort supplied to matching; matched and unmatched count retained and unmatched patients; pairs is the number of matched pairs. Matching used 1:1 nearest neighbours without replacement, a caliper of 0.2 standard deviations of the logit propensity score, and exact matching on calendar period"
)
```

Create the 2017+ relapse subset after matching across all years.

```{r}
relapse_data_2017 <- relapse_data |>
  dplyr::filter(calendar_year >= 2017) |>
  data.frame()

matched_relapse_2017 <- matched_relapse |>
  dplyr::filter(calendar_year >= 2017) |>
  data.frame()

relapse_matching_counts_2017 <- data.frame(
  eligible = nrow(relapse_data_2017),
  matched = nrow(matched_relapse_2017),
  unmatched = nrow(relapse_data_2017) - nrow(matched_relapse_2017),
  pairs = dplyr::n_distinct(matched_relapse_2017$subclass)
)
kableExtra::kable(
  relapse_matching_counts_2017,
  caption = "2017+ relapse cohort after all-years matching. eligible counts patients with an identified initial pathogen before matching; matched and unmatched count patients retained and not retained by the original matching; pairs counts retained matched pairs. No matching is repeated within 2017+"
)
```

## Relapse after matching, all

### Balance, all

Check balance

```{r, fig.height=6.7, fig.width=6.1}
#| fig-cap: "Figure 21. All years. Covariate balance before and after matching. Points show absolute standardized mean differences, standardized by the pre-matching short-treatment group in the displayed cohort; colours distinguish before and after matching. The dashed line marks 0.1. Original all-years matching weights are retained; no rematching is performed. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury. Obstruction risk factors is the umbrella category; subvesical obstruction includes urethral stricture. Ureteral stent denotes a stent in situ at discharge"

relapse_balance_all <- summary(
  match_relapse,
  standardize = TRUE
)

relapse_before_all <- as.data.frame(
  relapse_balance_all$sum.all,
  check.names = FALSE
) |>
  tibble::rownames_to_column("covariate") |>
  janitor::clean_names() |>
  dplyr::mutate(stage = "Before matching") |>
  data.frame()

relapse_after_all <- as.data.frame(
  relapse_balance_all$sum.matched,
  check.names = FALSE
) |>
  tibble::rownames_to_column("covariate") |>
  janitor::clean_names() |>
  dplyr::mutate(stage = "After matching") |>
  data.frame()

relapse_balance_plot_all <- dplyr::bind_rows(
  relapse_before_all,
  relapse_after_all
) |>
  dplyr::filter(covariate != "distance") |>
  data.frame()

myplot <- ggplot(
  relapse_balance_plot_all,
  aes(abs(std_mean_diff), covariate, colour = stage)
) +
  geom_vline(xintercept = 0.1, linetype = "dashed", colour = "grey50") +
  geom_point() +
  scale_y_discrete(labels = function(x) {
    dplyr::coalesce(unname(plot_labels_dict[x]), x)
  }) +
  scale_colour_manual(values = c("#A65F35", "#477DA0")) +
  labs(x = "Absolute standardized mean difference", y = NULL,
       colour = NULL)

plotac <- "fig_x21"
myplot <- save_plot(myplot, plotac, width = 6.1, height = 6.7)
myplot
```

### Relapse frequencies

Show relapse counts and proportions in the matched groups.

```{r}
relapse_counts_all <- matched_relapse |>
  dplyr::group_by(treatment_group) |>
  dplyr::summarise(
    patients = dplyr::n(),
    known_outcome = sum(!is.na(relapse_30D)),
    unknown_outcome = sum(is.na(relapse_30D)),
    relapses = sum(relapse_30D == 1, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    relapse_percent = 100 * relapses / known_outcome
  ) |>
  data.frame()

kableExtra::kable(
  relapse_counts_all,
  digits = 1,
  caption = "All years. Relapse within 30 days after therapy completion by sensitivity ATB duration in the matched cohort. patients counts matched patients; known_outcome and unknown_outcome count available and missing relapse outcomes; relapses counts events; relapse_percent is the percentage with relapse among patients with known outcomes"
)
```

### KM relapse

Estimate relapse-free survival through day 90 and HRs separately for 30 and 90 days

Patients without relapse are administratively censored at the respective follow-up limit. As in the preceding relapse analysis, a recorded recurrence with a discordant pathogen is not counted as relapse and does not trigger censoring. This uses the recorded recurrent episode and does not reconstruct subsequent infections.

```{r}
matched_relapse_survival_all <- matched_relapse |>
  dplyr::mutate(
    relapse_group = factor(
      treatment_under14D,
      levels = c(0, 1),
      labels = c("Long (>13 days)", "Short (<=13 days)")
    ),
    relapse_90D = dplyr::case_when(
      recurence_till_90D == 0 ~ 0,
      recurence_till_90D == 1 & hemoculture_agreed == 1 ~ 1,
      recurence_till_90D == 1 & hemoculture_agreed == 0 ~ 0,
      TRUE ~ NA_real_
    ),
    relapse_time_30D = dplyr::case_when(
      relapse_30D == 1 ~
        as.numeric(Infection_to90D_day - EndDate_therapy),
      relapse_30D == 0 ~ 30,
      TRUE ~ NA_real_
    ),
    relapse_time_90D = dplyr::case_when(
      relapse_90D == 1 ~
        as.numeric(Infection_to90D_day - EndDate_therapy),
      relapse_90D == 0 ~ 90,
      TRUE ~ NA_real_
    )
  ) |>
  data.frame()

km_relapse_90D_all <- survfit(
  Surv(relapse_time_90D, relapse_90D) ~ relapse_group,
  data = matched_relapse_survival_all,
  conf.type = "log-log"
)
```

#### HR, 30D and 90D

Fit each model separately. The 90-day estimate covers the entire period from day 0 to day 90, not only days 31–90.

```{r}
m_cox_relapse_30D_all <- coxph(
  Surv(relapse_time_30D, relapse_30D) ~ treatment_under14D,
  data = matched_relapse_survival_all,
  cluster = subclass
)

m_cox_relapse_90D_all <- coxph(
  Surv(relapse_time_90D, relapse_90D) ~ treatment_under14D,
  data = matched_relapse_survival_all,
  cluster = subclass
)

relapse_cox_summary_30D_all <- summary(m_cox_relapse_30D_all)
relapse_cox_summary_90D_all <- summary(m_cox_relapse_90D_all)

relapse_hr_30D_all <- data.frame(
  window = "0–30 days",
  comparison = "<=13 versus >13 days",
  n = m_cox_relapse_30D_all$n,
  events = m_cox_relapse_30D_all$nevent,
  HR = relapse_cox_summary_30D_all$conf.int[, "exp(coef)"],
  lower = relapse_cox_summary_30D_all$conf.int[, "lower .95"],
  upper = relapse_cox_summary_30D_all$conf.int[, "upper .95"],
  p_value = relapse_cox_summary_30D_all$coefficients[, "Pr(>|z|)"],
  row.names = NULL
)

relapse_hr_90D_all <- data.frame(
  window = "0–90 days",
  comparison = "<=13 versus >13 days",
  n = m_cox_relapse_90D_all$n,
  events = m_cox_relapse_90D_all$nevent,
  HR = relapse_cox_summary_90D_all$conf.int[, "exp(coef)"],
  lower = relapse_cox_summary_90D_all$conf.int[, "lower .95"],
  upper = relapse_cox_summary_90D_all$conf.int[, "upper .95"],
  p_value = relapse_cox_summary_90D_all$coefficients[, "Pr(>|z|)"],
  row.names = NULL
)

relapse_hr_table_all <- dplyr::bind_rows(
  relapse_hr_30D_all,
  relapse_hr_90D_all
) |>
  data.frame()

kableExtra::kable(
  relapse_hr_table_all,
  digits = 3,
  caption = "All years. Relapse within 30 and 90 days after therapy completion in the matched cohort with an identified initial pathogen. Separate Cox proportional hazards models included treatment group as the sole predictor, with robust variance clustered by matched pair. window identifies the period analysed; comparison gives the direction of the treatment contrast. HR states how many times the relapse hazard changes from >13 to <=13 days of sensitivity ATB treatment; HR >1 indicates a higher hazard with shorter treatment. n is the number analysed; events counts relapses; lower and upper are robust Wald 95% confidence limits; p_value is the two-sided robust Wald p-value. The 30-day analysis is primary and the 90-day analysis secondary; p-values are not adjusted for multiple testing"
)
```

#### Pair-stratified log-rank test

Compare the survival curves over the full 90-day follow-up using a log-rank test stratified by matched pair.

```{r}
logrank_relapse_90D_all <- survdiff(
  Surv(relapse_time_90D, relapse_90D) ~
    relapse_group +
    strata(subclass),
  data = matched_relapse_survival_all,
  rho = 0
)

relapse_logrank_p_all <- pchisq(
  logrank_relapse_90D_all$chisq,
  df = 1,
  lower.tail = FALSE
)

relapse_logrank_table_all <- data.frame(
  n = sum(logrank_relapse_90D_all$n),
  events = sum(logrank_relapse_90D_all$obs),
  chi_squared = logrank_relapse_90D_all$chisq,
  df = 1,
  p_value = relapse_logrank_p_all
)

kableExtra::kable(
  relapse_logrank_table_all,
  digits = 3,
  caption = "All years. Comparison of relapse-free survival through 90 days after therapy completion using a log-rank test stratified by matched pair. n is the number analysed; events counts relapses; chi_squared is the test statistic; df is its degrees of freedom; p_value tests equality of the survival curves and is distinct from the Cox model Wald p-values"
)
```

#### Post-hoc comparisons at days 30 and 90

Compare relapse proportions within matched pairs at both follow-up times.

```{r}
relapse_pairs_all <- matched_relapse_survival_all |>
  dplyr::transmute(
    subclass,
    treatment = dplyr::if_else(
      treatment_under14D == 1, "short", "long"
    ),
    relapse_30D,
    relapse_90D
  ) |>
  tidyr::pivot_longer(
    cols = c(relapse_30D, relapse_90D),
    names_to = "outcome",
    values_to = "event"
  ) |>
  dplyr::mutate(
    day = dplyr::if_else(outcome == "relapse_30D", 30, 90)
  ) |>
  dplyr::select(-outcome) |>
  tidyr::pivot_wider(
    names_from = treatment,
    values_from = event
  ) |>
  data.frame()

relapse_posthoc_all <- relapse_pairs_all |>
  dplyr::group_by(day) |>
  dplyr::summarise(
    pairs = sum(!is.na(short) & !is.na(long)),
    incomplete_pairs = sum(is.na(short) | is.na(long)),
    short_only = sum(short == 1 & long == 0, na.rm = TRUE),
    long_only = sum(short == 0 & long == 1, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::rowwise() |>
  dplyr::mutate(
    p_value = if (pairs == 0) {
      NA_real_
    } else if (short_only + long_only == 0) {
      1
    } else {
      binom.test(
        short_only,
        short_only + long_only,
        p = 0.5,
        alternative = "two.sided"
      )$p.value
    }
  ) |>
  dplyr::ungroup() |>
  dplyr::mutate(
    p_holm = p.adjust(p_value, method = "holm", n = 2)
  ) |>
  dplyr::arrange(day) |>
  data.frame()

kableExtra::kable(
  relapse_posthoc_all,
  digits = 3,
  caption = "All years. Post-hoc comparisons of relapse within 30 and 90 days after therapy completion in the matched cohort. day is the follow-up limit; pairs counts matched pairs with both outcomes known; incomplete_pairs counts pairs not used in that comparison because at least one outcome is missing. short_only and long_only count pairs with relapse only in the patient treated for <=13 or >13 days, respectively. p_value is the two-sided exact McNemar p-value; p_holm applies Holm adjustment across the two comparisons"
)
```

#### Survival curves

```{r, fig.height=5.5, fig.width=6}
#| fig-cap: "Figure 22. All years. Relapse-free survival through 90 days after therapy completion in propensity-score-matched patients with an identified initial pathogen. Relapse requires recurrence with concordant pathogens. Curves are Kaplan–Meier estimates; shaded regions show pointwise 95% confidence intervals based on Greenwood variance with a log-log transformation. Tick marks indicate censoring, the vertical dashed line marks day 30, and the table shows numbers at risk. The overall p-value is from a log-rank test stratified by matched pair over 90 days; post-hoc p-values compare relapse proportions by days 30 and 90 using two-sided exact McNemar tests with Holm adjustment across these two comparisons. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro"

relapse_p_text_all <- paste0(
  "Pair-stratified log-rank p = ",
  format.pval(relapse_logrank_p_all, digits = 3, eps = 0),
  "\nDay 30, post-hoc p (Holm) = ",
  format.pval(
    relapse_posthoc_all$p_holm[relapse_posthoc_all$day == 30],
    digits = 3,
    eps = 0
  ),
  "\nDay 90, post-hoc p (Holm) = ",
  format.pval(
    relapse_posthoc_all$p_holm[relapse_posthoc_all$day == 90],
    digits = 3,
    eps = 0
  )
)

myplot <- survminer::ggsurvplot(
  km_relapse_90D_all,
  data = matched_relapse_survival_all,
  pval = relapse_p_text_all,
  pval.coord = c(40, 0.15),
  pval.size = 3.7,
  conf.int = TRUE,
  risk.table = TRUE,
  risk.table.y.text.col = FALSE,
  risk.table.fontsize = 3.6,
  censor.shape = 124,
  censor.size = 2,
  palette = c("#477DA0", "#A65F35"),
  xlab = "Days from the end of therapy",
  ylab = "Probability of remaining relapse-free",
  legend.title = "Therapy duration",
  legend.labs = c("Long (>13 days)", "Short (<=13 days)"),
  break.time.by = 15,
  xlim = c(0, 90),
  ggtheme = theme_grey()
)

myplot$plot <- myplot$plot +
  theme(
    plot.title = element_text(size = 12),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11)
  ) +
  geom_vline(
    xintercept = 30,
    linetype = "dashed",
    colour = "grey50"
  )

myplot$table <- myplot$table +
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11)
  )

myplot <- cowplot::plot_grid(
  myplot$plot,
  myplot$table + theme(legend.position = "none"),
  ncol = 1,
  rel_heights = c(0.75, 0.25),
  align = "v",
  axis = "lr"
)

plotac <- "fig_x22_relapse_survival_90D_all"
myplot <- save_plot(myplot, plotac, width = 6, height = 5.5)
myplot
```

#### HR

```{r}
relapse_hr_table_all <- dplyr::bind_rows(
  relapse_hr_30D_all,
  relapse_hr_90D_all
) |>
  data.frame()

kableExtra::kable(
  relapse_hr_table_all,
  digits = 3,
  caption = "All years. Relapse hazard ratios from separate treatment-only Cox models covering days 0–30 and 0–90 after therapy completion, with robust variance clustered by matched pair. window identifies the follow-up interval; comparison specifies the treatment contrast. HR states how many times the relapse hazard changes from >13 to <=13 days of sensitivity ATB therapy; HR >1 indicates higher hazard with shorter treatment. n is the number of patients analysed; events counts relapses; lower and upper are the robust Wald 95% confidence limits; p_value is the two-sided robust Wald p-value without multiplicity adjustment"
)
```

## Relapse after matching, 2017+

### Balance, 2017+

Check balance

```{r, fig.height=6.7, fig.width=6.1}
#| fig-cap: "Figure 23. 2017+. Covariate balance before and after matching. Points show absolute standardized mean differences, standardized by the pre-matching short-treatment group in the displayed cohort; colours distinguish before and after matching. The dashed line marks 0.1. Original all-years matching weights are retained; no rematching is performed. TX denotes transplantation, MDR multidrug resistance, ATB antibiotics and AKI acute kidney injury. Obstruction risk factors is the umbrella category; subvesical obstruction includes urethral stricture. Ureteral stent denotes a stent in situ at discharge"

relapse_keep_2017 <- relapse_data$calendar_year >= 2017
match_relapse_balance_2017 <- match_relapse
match_relapse_balance_2017$X <- match_relapse$X[
  relapse_keep_2017, , drop = FALSE
]
match_relapse_balance_2017$treat <- match_relapse$treat[
  relapse_keep_2017
]
match_relapse_balance_2017$weights <- match_relapse$weights[
  relapse_keep_2017
]
match_relapse_balance_2017$distance <- match_relapse$distance[
  relapse_keep_2017
]
match_relapse_balance_2017$discarded <- match_relapse$discarded[
  relapse_keep_2017
]
match_relapse_balance_2017$subclass <- match_relapse$subclass[
  relapse_keep_2017
]
match_relapse_balance_2017$match.matrix <- match_relapse$match.matrix[
  rownames(match_relapse$match.matrix) %in%
    names(match_relapse_balance_2017$treat), , drop = FALSE
]

relapse_balance_2017 <- summary(
  match_relapse_balance_2017,
  standardize = TRUE
)

relapse_before_2017 <- as.data.frame(
  relapse_balance_2017$sum.all,
  check.names = FALSE
) |>
  tibble::rownames_to_column("covariate") |>
  janitor::clean_names() |>
  dplyr::mutate(stage = "Before matching") |>
  data.frame()

relapse_after_2017 <- as.data.frame(
  relapse_balance_2017$sum.matched,
  check.names = FALSE
) |>
  tibble::rownames_to_column("covariate") |>
  janitor::clean_names() |>
  dplyr::mutate(stage = "After matching") |>
  data.frame()

relapse_balance_plot_2017 <- dplyr::bind_rows(
  relapse_before_2017,
  relapse_after_2017
) |>
  dplyr::filter(covariate != "distance") |>
  data.frame()

myplot <- ggplot(
  relapse_balance_plot_2017,
  aes(abs(std_mean_diff), covariate, colour = stage)
) +
  geom_vline(xintercept = 0.1, linetype = "dashed", colour = "grey50") +
  geom_point() +
  scale_y_discrete(labels = function(x) {
    dplyr::coalesce(unname(plot_labels_dict[x]), x)
  }) +
  scale_colour_manual(values = c("#A65F35", "#477DA0")) +
  labs(x = "Absolute standardized mean difference", y = NULL,
       colour = NULL)

plotac <- "fig_x23_relapse_2017plus"
myplot <- save_plot(myplot, plotac, width = 6.1, height = 6.7)
myplot
```

### Relapse frequencies

Show relapse counts and proportions in the matched groups.

```{r}
relapse_counts_2017 <- matched_relapse_2017 |>
  dplyr::group_by(treatment_group) |>
  dplyr::summarise(
    patients = dplyr::n(),
    known_outcome = sum(!is.na(relapse_30D)),
    unknown_outcome = sum(is.na(relapse_30D)),
    relapses = sum(relapse_30D == 1, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    relapse_percent = 100 * relapses / known_outcome
  ) |>
  data.frame()

kableExtra::kable(
  relapse_counts_2017,
  digits = 1,
  caption = "2017+. Relapse within 30 days after therapy completion by sensitivity ATB duration in the matched cohort. patients counts matched patients; known_outcome and unknown_outcome count available and missing relapse outcomes; relapses counts events; relapse_percent is the percentage with relapse among patients with known outcomes"
)
```

### KM relapse

Estimate relapse-free survival through day 90 and HRs separately for 30 and 90 days

Patients without relapse are administratively censored at the respective follow-up limit. As in the preceding relapse analysis, a recorded recurrence with a discordant pathogen is not counted as relapse and does not trigger censoring. This uses the recorded recurrent episode and does not reconstruct subsequent infections.

```{r}
matched_relapse_survival_2017 <- matched_relapse_2017 |>
  dplyr::mutate(
    relapse_group = factor(
      treatment_under14D,
      levels = c(0, 1),
      labels = c("Long (>13 days)", "Short (<=13 days)")
    ),
    relapse_90D = dplyr::case_when(
      recurence_till_90D == 0 ~ 0,
      recurence_till_90D == 1 & hemoculture_agreed == 1 ~ 1,
      recurence_till_90D == 1 & hemoculture_agreed == 0 ~ 0,
      TRUE ~ NA_real_
    ),
    relapse_time_30D = dplyr::case_when(
      relapse_30D == 1 ~
        as.numeric(Infection_to90D_day - EndDate_therapy),
      relapse_30D == 0 ~ 30,
      TRUE ~ NA_real_
    ),
    relapse_time_90D = dplyr::case_when(
      relapse_90D == 1 ~
        as.numeric(Infection_to90D_day - EndDate_therapy),
      relapse_90D == 0 ~ 90,
      TRUE ~ NA_real_
    )
  ) |>
  data.frame()

km_relapse_90D_2017 <- survfit(
  Surv(relapse_time_90D, relapse_90D) ~ relapse_group,
  data = matched_relapse_survival_2017,
  conf.type = "log-log"
)
```

#### HR, 30D and 90D

Fit each model separately. The 90-day estimate covers the entire period from day 0 to day 90, not only days 31–90.

```{r}
m_cox_relapse_30D_2017 <- coxph(
  Surv(relapse_time_30D, relapse_30D) ~ treatment_under14D,
  data = matched_relapse_survival_2017,
  cluster = subclass
)

m_cox_relapse_90D_2017 <- coxph(
  Surv(relapse_time_90D, relapse_90D) ~ treatment_under14D,
  data = matched_relapse_survival_2017,
  cluster = subclass
)

relapse_cox_summary_30D_2017 <- summary(m_cox_relapse_30D_2017)
relapse_cox_summary_90D_2017 <- summary(m_cox_relapse_90D_2017)

relapse_hr_30D_2017 <- data.frame(
  window = "0–30 days",
  comparison = "<=13 versus >13 days",
  n = m_cox_relapse_30D_2017$n,
  events = m_cox_relapse_30D_2017$nevent,
  HR = relapse_cox_summary_30D_2017$conf.int[, "exp(coef)"],
  lower = relapse_cox_summary_30D_2017$conf.int[, "lower .95"],
  upper = relapse_cox_summary_30D_2017$conf.int[, "upper .95"],
  p_value = relapse_cox_summary_30D_2017$coefficients[, "Pr(>|z|)"],
  row.names = NULL
)

relapse_hr_90D_2017 <- data.frame(
  window = "0–90 days",
  comparison = "<=13 versus >13 days",
  n = m_cox_relapse_90D_2017$n,
  events = m_cox_relapse_90D_2017$nevent,
  HR = relapse_cox_summary_90D_2017$conf.int[, "exp(coef)"],
  lower = relapse_cox_summary_90D_2017$conf.int[, "lower .95"],
  upper = relapse_cox_summary_90D_2017$conf.int[, "upper .95"],
  p_value = relapse_cox_summary_90D_2017$coefficients[, "Pr(>|z|)"],
  row.names = NULL
)

relapse_hr_table_2017 <- dplyr::bind_rows(
  relapse_hr_30D_2017,
  relapse_hr_90D_2017
) |>
  data.frame()

kableExtra::kable(
  relapse_hr_table_2017,
  digits = 3,
  caption = "2017+. Relapse within 30 and 90 days after therapy completion in the matched cohort with an identified initial pathogen. Separate Cox proportional hazards models included treatment group as the sole predictor, with robust variance clustered by matched pair. window identifies the period analysed; comparison gives the direction of the treatment contrast. HR states how many times the relapse hazard changes from >13 to <=13 days of sensitivity ATB treatment; HR >1 indicates a higher hazard with shorter treatment. n is the number analysed; events counts relapses; lower and upper are robust Wald 95% confidence limits; p_value is the two-sided robust Wald p-value. The 30-day analysis is primary and the 90-day analysis secondary; p-values are not adjusted for multiple testing"
)
```

#### Pair-stratified log-rank test

Compare the survival curves over the full 90-day follow-up using a log-rank test stratified by matched pair.

```{r}
logrank_relapse_90D_2017 <- survdiff(
  Surv(relapse_time_90D, relapse_90D) ~
    relapse_group +
    strata(subclass),
  data = matched_relapse_survival_2017,
  rho = 0
)

relapse_logrank_p_2017 <- pchisq(
  logrank_relapse_90D_2017$chisq,
  df = 1,
  lower.tail = FALSE
)

relapse_logrank_table_2017 <- data.frame(
  n = sum(logrank_relapse_90D_2017$n),
  events = sum(logrank_relapse_90D_2017$obs),
  chi_squared = logrank_relapse_90D_2017$chisq,
  df = 1,
  p_value = relapse_logrank_p_2017
)

kableExtra::kable(
  relapse_logrank_table_2017,
  digits = 3,
  caption = "2017+. Comparison of relapse-free survival through 90 days after therapy completion using a log-rank test stratified by matched pair. n is the number analysed; events counts relapses; chi_squared is the test statistic; df is its degrees of freedom; p_value tests equality of the survival curves and is distinct from the Cox model Wald p-values"
)
```

#### Post-hoc comparisons at days 30 and 90


```{r}
relapse_pairs_2017 <- matched_relapse_survival_2017 |>
  dplyr::transmute(
    subclass,
    treatment = dplyr::if_else(
      treatment_under14D == 1, "short", "long"
    ),
    relapse_30D,
    relapse_90D
  ) |>
  tidyr::pivot_longer(
    cols = c(relapse_30D, relapse_90D),
    names_to = "outcome",
    values_to = "event"
  ) |>
  dplyr::mutate(
    day = dplyr::if_else(outcome == "relapse_30D", 30, 90)
  ) |>
  dplyr::select(-outcome) |>
  tidyr::pivot_wider(
    names_from = treatment,
    values_from = event
  ) |>
  data.frame()

relapse_posthoc_2017 <- relapse_pairs_2017 |>
  dplyr::group_by(day) |>
  dplyr::summarise(
    pairs = sum(!is.na(short) & !is.na(long)),
    incomplete_pairs = sum(is.na(short) | is.na(long)),
    short_only = sum(short == 1 & long == 0, na.rm = TRUE),
    long_only = sum(short == 0 & long == 1, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::rowwise() |>
  dplyr::mutate(
    p_value = if (pairs == 0) {
      NA_real_
    } else if (short_only + long_only == 0) {
      1
    } else {
      binom.test(
        short_only,
        short_only + long_only,
        p = 0.5,
        alternative = "two.sided"
      )$p.value
    }
  ) |>
  dplyr::ungroup() |>
  dplyr::mutate(
    p_holm = p.adjust(p_value, method = "holm", n = 2)
  ) |>
  dplyr::arrange(day) |>
  data.frame()

kableExtra::kable(
  relapse_posthoc_2017,
  digits = 3,
  caption = "2017+. Post-hoc comparisons of relapse within 30 and 90 days after therapy completion in the matched cohort. day is the follow-up limit; pairs counts matched pairs with both outcomes known; incomplete_pairs counts pairs not used in that comparison because at least one outcome is missing. short_only and long_only count pairs with relapse only in the patient treated for <=13 or >13 days, respectively. p_value is the two-sided exact McNemar p-value; p_holm applies Holm adjustment across the two comparisons"
)
```

#### Survival curves


```{r, fig.height=5.5, fig.width=6}
#| fig-cap: "Figure 24. 2017+. Relapse-free survival through 90 days after therapy completion in propensity-score-matched patients with an identified initial pathogen. Relapse requires recurrence with concordant pathogens. Curves are Kaplan–Meier estimates; shaded regions show pointwise 95% confidence intervals based on Greenwood variance with a log-log transformation. Tick marks indicate censoring, the vertical dashed line marks day 30, and the table shows numbers at risk. The overall p-value is from a log-rank test stratified by matched pair over 90 days; post-hoc p-values compare relapse proportions by days 30 and 90 using two-sided exact McNemar tests with Holm adjustment across these two comparisons. Therapy duration denotes days of treatment with an antibiotic to which the isolated organism was susceptible in vitro"

relapse_p_text_2017 <- paste0(
  "Pair-stratified log-rank p = ",
  format.pval(relapse_logrank_p_2017, digits = 3, eps = 0),
  "\nDay 30, post-hoc p (Holm) = ",
  format.pval(
    relapse_posthoc_2017$p_holm[relapse_posthoc_2017$day == 30],
    digits = 3,
    eps = 0
  ),
  "\nDay 90, post-hoc p (Holm) = ",
  format.pval(
    relapse_posthoc_2017$p_holm[relapse_posthoc_2017$day == 90],
    digits = 3,
    eps = 0
  )
)

myplot <- survminer::ggsurvplot(
  km_relapse_90D_2017,
  data = matched_relapse_survival_2017,
  pval = relapse_p_text_2017,
  pval.coord = c(40, 0.15),
  pval.size = 3.7,
  conf.int = TRUE,
  risk.table = TRUE,
  risk.table.y.text.col = FALSE,
  risk.table.fontsize = 3.6,
  censor.shape = 124,
  censor.size = 2,
  palette = c("#477DA0", "#A65F35"),
  xlab = "Days from the end of therapy",
  ylab = "Probability of remaining relapse-free",
  legend.title = "Therapy duration",
  legend.labs = c("Long (>13 days)", "Short (<=13 days)"),
  break.time.by = 15,
  xlim = c(0, 90),
  ggtheme = theme_grey()
)

myplot$plot <- myplot$plot +
  theme(
    plot.title = element_text(size = 12),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11)
  ) +
  geom_vline(
    xintercept = 30,
    linetype = "dashed",
    colour = "grey50"
  )

myplot$table <- myplot$table +
  theme(
    plot.title = element_text(size = 11),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11)
  )

myplot <- cowplot::plot_grid(
  myplot$plot,
  myplot$table + theme(legend.position = "none"),
  ncol = 1,
  rel_heights = c(0.75, 0.25),
  align = "v",
  axis = "lr"
)

plotac <- "fig_x24"
myplot <- save_plot(myplot, plotac, width = 6, height = 5.5)
myplot
```

# Safety outcomes

Report patient proportions within 30 and 90 days after therapy completion in the full and primary matched cohorts, with the same analyses for 2017+. Events on or before therapy completion are excluded. Empty source entries retain the agreed coding of no event. An affirmative 90-day readmission entry without a date is counted at 90 days, but its 30-day status remains unknown. A recorded clostridial infection without a date cannot establish a post-treatment event and is reported as unknown. No dates are imputed.

## Available timing

Show records that cannot be assigned to a post-treatment window. Dates on the final treatment day are shown separately because their within-day order is unknown.

```{r}
safety_timing <- data_analysis |>
  dplyr::summarise(
    clostridium_positive_without_date = sum(
      clostridium == 1 & is.na(ClostridiumDate), na.rm = TRUE
    ),
    uti_readmission_positive_without_date = sum(
      readmission_90d_uti == 1 & is.na(ReadmissionDate_uti),
      na.rm = TRUE
    ),
    other_readmission_positive_without_date = sum(
      readmission_90d_other == 1 & is.na(ReadmissionDate_other),
      na.rm = TRUE
    ),
    clostridium_on_final_treatment_day = sum(
      clostridium_days_after_therapy == 0, na.rm = TRUE
    ),
    clostridium_before_therapy_end = sum(
      clostridium_days_after_therapy < 0, na.rm = TRUE
    )
  ) |>
  tidyr::pivot_longer(
    dplyr::everything(),
    names_to = "timing_issue",
    values_to = "patients"
  ) |>
  data.frame()

kableExtra::kable(
  safety_timing,
  caption = "Safety timing. timing_issue identifies positive records without an event date or clostridial infections occurring on or before the final treatment day; patients counts affected records. These records are retained in the cohort, but unknown timing is not recoded as absence"
)
```

## Summary function

Use the same definitions and denominators in each cohort. Any readmission means at least one UTI-related or other recorded readmission, with each patient counted once.

```{r}
safety_labels <- c(
  clostridium_30D = "Clostridial infection, 30 days",
  clostridium_90D = "Clostridial infection, 90 days",
  readmission_uti_30D = "Readmission for UTI, 30 days",
  readmission_uti_90D = "Readmission for UTI, 90 days",
  readmission_other_30D = "Readmission for another reason, 30 days",
  readmission_other_90D = "Readmission for another reason, 90 days",
  readmission_any_30D = "Any readmission, 30 days",
  readmission_any_90D = "Any readmission, 90 days"
)

safety_table <- function(data) {
  data |>
    dplyr::select(
      treatment_group,
      dplyr::all_of(names(safety_labels))
    ) |>
    tidyr::pivot_longer(
      -treatment_group,
      names_to = "outcome",
      values_to = "event"
    ) |>
    dplyr::group_by(
      treatment_group,
      outcome
    ) |>
    dplyr::summarise(
      patients = dplyr::n(),
      known = sum(!is.na(event)),
      unknown = sum(is.na(event)),
      events = sum(event == 1, na.rm = TRUE),
      percent = 100 * events / known,
      .groups = "drop"
    ) |>
    dplyr::mutate(
      outcome = factor(
        outcome,
        levels = names(safety_labels),
        labels = unname(safety_labels)
      )
    ) |>
    dplyr::arrange(
      outcome,
      treatment_group
    ) |>
    data.frame()
}
```

## Full cohort, all

Show safety outcomes in all analysed patients.

```{r}
safety_all <- safety_table(data_analysis)
kableExtra::kable(
  safety_all,
  digits = 1,
  caption = "Safety outcomes after therapy completion, full cohort. treatment_group compares sensitivity ATB duration <=13 with >13 days; outcome specifies the event and follow-up window. patients is the group size, known and unknown count assessable and unassessable outcomes, events is the number affected, and percent is 100 × events/known. These are patient proportions, not person-time incidence rates"
)
```

## Matched cohort, all

Show safety outcomes in the original 1:1 matched pairs.

```{r}
safety_matched_all <- safety_table(matched_data)
kableExtra::kable(
  safety_matched_all,
  digits = 1,
  caption = "Safety outcomes after therapy completion, primary matched cohort. treatment_group compares sensitivity ATB duration <=13 with >13 days; outcome specifies the event and follow-up window. patients is the group size, known and unknown count assessable and unassessable outcomes, events is the number affected, and percent is 100 × events/known. Original matched pairs are retained"
)
```

## Full cohort, 2017+

Show the same outcomes among patients treated from 2017 onward.

```{r}
safety_2017 <- safety_table(data_2017)
kableExtra::kable(
  safety_2017,
  digits = 1,
  caption = "Safety outcomes after therapy completion, full cohort treated from 2017 onward. treatment_group compares sensitivity ATB duration <=13 with >13 days; outcome specifies the event and follow-up window. patients is the group size, known and unknown count assessable and unassessable outcomes, events is the number affected, and percent is 100 × events/known"
)
```

## Matched cohort, 2017+

Retain the existing matched pairs from 2017 onward.

```{r}
safety_matched_2017 <- safety_table(matched_data_2017)
kableExtra::kable(
  safety_matched_2017,
  digits = 1,
  caption = "Safety outcomes after therapy completion, primary matched cohort treated from 2017 onward. treatment_group compares sensitivity ATB duration <=13 with >13 days; outcome specifies the event and follow-up window. patients is the group size, known and unknown count assessable and unassessable outcomes, events is the number affected, and percent is 100 × events/known. This subset retains the all-years matches without rematching"
)
```

# Secondary CCW analysis

```{r}
ccw_input <- data_analysis
ccw_outcomes <- c("recurence_till_1M", "recurence_till_90D")

ccw_baseline_vars <- c(
  "sex_female", "age_by30y", "log2_TX_to_infection",
  "diabetes_severe", "mra_positive", "hemoculture_positive",
  "profylaxis", "severe_aki", "CRP_entry_by100",
  "past_urol_instrumentation", "immunosuppression_regimen",
  "depletion_induction_or_rejection_treatment_6M", "calendar_period"
)
ccw_bm_br_vars <- c(
  "fever_before_planned_ATB_stop",
  "clinical_worsening_before_planned_ATB_stop",
  "urine_findings_worsening_before_planned_ATB_stop",
  "ATB_extension_CRP_dynamics",
  "ATB_extension_other_reason",
  "ATB_extension_urologic_procedure"
)
ccw_variables <- c(
  "ID", "ATB_sensitivity_duration", "treatment_under14D",
  ccw_baseline_vars, ccw_bm_br_vars,
  ccw_outcomes
)

ccw_missing <- ccw_input |>
  dplyr::summarise(
    dplyr::across(
      all_of(ccw_variables),
      ~ sum(is.na(.x))
    )
  ) |>
  tidyr::pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "missing_n"
  ) |>
  dplyr::mutate(
    missing_percent = 100 * missing_n / nrow(ccw_input)
  ) |>
  dplyr::arrange(desc(missing_n)) |>
  data.frame()
kableExtra::kable(
  ccw_missing,
  digits = 1,
  caption = "Missing values in variables used by the CCW analysis. missing_n is the number of patients with NA; missing_percent is their percentage of the analysed cohort. Counts can overlap across variables. The agreed exclusion for missing entry CRP has already been applied"
)

ccw_sample <- ccw_input |>
  dplyr::summarise(
    patients_available = nrow(data_analysis),
    excluded_missing_CRP = sum(is.na(data_analysis$CRP_entry)),
    patients_included = dplyr::n(),
    patients_with_any_NA = sum(dplyr::if_any(
      all_of(ccw_variables),
      is.na
    ))
  ) |>
  dplyr::mutate(
    patients_without_NA = patients_included - patients_with_any_NA
  ) |>
  data.frame()
kableExtra::kable(
  ccw_sample,
  caption = "Analysis sample. patients_available counts the original cohort; excluded_missing_CRP counts patients excluded for missing entry CRP; patients_included counts those retained. patients_with_any_NA and patients_without_NA count retained patients with and without missing analysis inputs, respectively"
)
```


Calculate weighted recurrence risks

```{r}
ccw_risks <- function(endpoints) {
  endpoints |>
    dplyr::select(
      strategy,
      weight,
      dplyr::all_of(ccw_outcomes)
    ) |>
    tidyr::pivot_longer(
      cols = dplyr::all_of(ccw_outcomes),
      names_to = "outcome",
      values_to = "event"
    ) |>
    dplyr::group_by(
      outcome,
      strategy
    ) |>
    dplyr::summarise(
      risk = weighted.mean(event, weight),
      .groups = "drop"
    ) |>
    tidyr::pivot_wider(
      names_from = strategy,
      values_from = risk
    ) |>
    dplyr::mutate(
      risk_difference = short - long,
      risk_ratio = short / long
    ) |>
    data.frame()
}
```

## Stopping by day 13

Model stopping by day 13 using the baseline and BM–BR covariates. The reference calendar period is 2008–2016

```{r}
m_stop_by13 <- glm(
  treatment_under14D ~
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    diabetes_severe +
    mra_positive +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    CRP_entry_by100 +
    past_urol_instrumentation +
    immunosuppression_regimen +
    depletion_induction_or_rejection_treatment_6M +
    calendar_period +
    fever_before_planned_ATB_stop +
    clinical_worsening_before_planned_ATB_stop +
    urine_findings_worsening_before_planned_ATB_stop +
    ATB_extension_CRP_dynamics +
    ATB_extension_other_reason +
    ATB_extension_urologic_procedure,
  data = ccw_input,
  family = binomial(link = "logit")
)
summary(m_stop_by13)
kableExtra::kable(
  data.frame(
    supplied = nrow(ccw_input),
    used = nobs(m_stop_by13),
    omitted = nrow(ccw_input) - nobs(m_stop_by13)
  ),
  caption = "Two-period stopping model: observations used. supplied and used count patients available and used in fitting; omitted is their difference"
)
sjPlot::tab_model(
  m_stop_by13,
  pred.labels = unname(
    my_labels_dict[names(coef(m_stop_by13))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "Probability model for stopping sensitivity ATB treatment by day 13. OR states how many times the odds of stopping change per one modelled unit increase or a change from 0 to 1; categorical effects are relative to the reference level. Intervals are 95% profile-likelihood limits and p-values are Wald tests"
)
```

## Weight the two periods

Calculate inverse-probability weights

```{r}
ccw_period_data <- ccw_input
ccw_period_data$p_short <- as.numeric(predict(
  m_stop_by13,
  newdata = ccw_period_data,
  type = "response"
))
ccw_endpoints_period <- ccw_period_data |>
  dplyr::mutate(
    strategy = dplyr::if_else(
      treatment_under14D == 1,
      "short",
      "long"
    ),
    weight = dplyr::if_else(
      treatment_under14D == 1,
      1 / p_short,
      1 / (1 - p_short)
    )
  ) |>
  data.frame()
```

Check weights and effective sample sizes

```{r}
weight_issues_period <- ccw_endpoints_period |>
  dplyr::filter(!is.finite(weight)) |>
  dplyr::mutate(
    issue = dplyr::case_when(
      is.na(p_short) ~ "Missing stopping prediction",
      TRUE ~ "Non-finite inverse-probability weight"
    )
  ) |>
  dplyr::select(
    ID,
    strategy,
    ATB_sensitivity_duration,
    CRP_entry_by100,
    p_short,
    weight,
    issue
  ) |>
  data.frame()
kableExtra::kable(
  weight_issues_period,
  digits = 3,
  caption = "Two-period approximation: patients with unavailable or infinite weights. ID is the analysis identifier; strategy is short or long treatment; ATB_sensitivity_duration is treatment duration in days; CRP_entry_by100 is entry CRP divided by 100; p_short is the predicted probability of stopping by day 13; weight is the final inverse-probability weight. issue distinguishes a missing prediction from another non-finite weight. An empty table means no such issues"
)

weight_summary_period <- ccw_endpoints_period |>
  dplyr::group_by(strategy) |>
  dplyr::summarise(
    patients = dplyr::n(),
    nonfinite_weights = sum(!is.finite(weight)),
    median_weight = median(weight[is.finite(weight)]),
    p99_weight = quantile(
      weight[is.finite(weight)], 0.99, na.rm = TRUE
    ),
    max_weight = quantile(
      weight[is.finite(weight)], 1, na.rm = TRUE
    ),
    ESS = sum(weight)^2 / sum(weight^2),
    .groups = "drop"
  ) |>
  data.frame()
kableExtra::kable(
  weight_summary_period,
  digits = 3,
  caption = "Two-period approximation: weight diagnostics. patients counts retained patients by strategy; nonfinite_weights counts undefined or infinite weights; median_weight, p99_weight and max_weight describe finite weights only. ESS is the squared sum of all weights divided by their sum of squares and is undefined if any weight is missing or infinite. No patient is excluded by this diagnostic summary"
)
```

## Weighted recurrence risks

Show weighted risks

```{r}
ccw_point_period <- ccw_risks(ccw_endpoints_period)
kableExtra::kable(
  ccw_point_period,
  digits = 3,
  caption = "Two-period approximation: recurrence after therapy completion. outcome identifies the 30-day or 90-day window; short and long are weighted risks after <=13 and >13 days of sensitivity ATB treatment. risk_difference is short minus long; risk_ratio is short divided by long"
)
```

## Patient bootstrap

Refit the stopping model and calculate risks in each patient resample

```{r}
bootstrap_ccw_period <- function() {
  sampled <- sample.int(nrow(ccw_input), replace = TRUE)
  boot_data <- ccw_input[sampled, , drop = FALSE]
  boot_data$ID <- as.character(seq_len(nrow(boot_data)))
  m_stop_boot <- update(m_stop_by13, data = boot_data)
  if (!m_stop_boot$converged) {
    stop("Period-level stopping model did not converge in this replicate.")
  }
  boot_data$p_short <- predict(
    m_stop_boot,
    newdata = boot_data,
    type = "response"
  )
  endpoints <- boot_data |>
    dplyr::mutate(
      strategy = dplyr::if_else(
        treatment_under14D == 1,
        "short",
        "long"
      ),
      weight = dplyr::if_else(
        treatment_under14D == 1,
        1 / p_short,
        1 / (1 - p_short)
      )
    ) |>
    data.frame()
  ccw_risks(endpoints)
}
```

Run 500 patient bootstrap replicates, reusing the existing cache if present

```{r}
modelac <- "ccw_results_v2_d13minusVSsd14plus"
run2(
  modelac,
  expr = {
    set.seed(seeding)
    purrr::map(seq_len(500), function(replicate_id) {
      tryCatch(
        list(
          result = bootstrap_ccw_period(),
          error = NA_character_
        ),
        error = function(e) list(
          result = ccw_point_period |>
            dplyr::mutate(
              dplyr::across(
                c(short, long, risk_difference, risk_ratio),
                ~ NA_real_
              )
            ) |>
            data.frame(),
          error = conditionMessage(e)
        )
      )
    })
  }
)
ccw_bootstrap_period <- get(modelac)
bootstrap_errors_period <- purrr::map_chr(
  ccw_bootstrap_period,
  "error"
)
bootstrap_status_period <- data.frame(
  requested = length(ccw_bootstrap_period),
  failed = sum(!is.na(bootstrap_errors_period))
)
kableExtra::kable(
  bootstrap_status_period,
  caption = "Two-period approximation: bootstrap execution. requested counts patient resamples; failed counts model-fitting errors or nonconvergence. Non-finite risk estimates are accounted for in valid_replicates in the results table"
)
unique(bootstrap_errors_period[!is.na(bootstrap_errors_period)])
bootstrap_results_period <- purrr::map_dfr(
  ccw_bootstrap_period,
  "result",
  .id = "replicate"
) |>
  data.frame()
```

Show estimates and percentile 95% confidence intervals

```{r}
bootstrap_limits_period <- bootstrap_results_period |>
  tidyr::pivot_longer(
    cols = c(short, long, risk_difference, risk_ratio),
    names_to = "estimand",
    values_to = "estimate"
  ) |>
  dplyr::group_by(
    outcome,
    estimand
  ) |>
  dplyr::summarise(
    valid_replicates = sum(is.finite(estimate)),
    lower = quantile(estimate[is.finite(estimate)], 0.025, na.rm = TRUE),
    upper = quantile(estimate[is.finite(estimate)], 0.975, na.rm = TRUE),
    .groups = "drop"
  ) |>
  data.frame()
ccw_table_period <- ccw_point_period |>
  tidyr::pivot_longer(
    cols = c(short, long, risk_difference, risk_ratio),
    names_to = "estimand",
    values_to = "estimate"
  ) |>
  dplyr::left_join(
    bootstrap_limits_period,
    by = c("outcome", "estimand")
  ) |>
  dplyr::mutate(
    lower = dplyr::if_else(is.finite(estimate), lower, NA_real_),
    upper = dplyr::if_else(is.finite(estimate), upper, NA_real_)
  ) |>
  data.frame()
kableExtra::kable(
  ccw_table_period,
  digits = 3,
  caption = "Two-period approximation: recurrence estimates after therapy completion. outcome identifies the 30-day or 90-day window; estimand identifies the short-treatment risk, long-treatment risk, risk difference (short minus long) or risk ratio (short divided by long). estimate is the point estimate; lower and upper are patient-bootstrap percentile 95% confidence limits. valid_replicates counts finite bootstrap estimates contributing to each interval"
)
```

# Secondary CCW analysis, 2017+

As above but only using data 2017+

```{r}
ccw_input <- data_analysis |> dplyr::filter(calendar_year >= 2017)

ccw_outcomes <- c("recurence_till_1M", "recurence_till_90D")

ccw_baseline_vars <- c(
  "sex_female", "age_by30y", "log2_TX_to_infection",
  "diabetes_severe", "mra_positive", "hemoculture_positive",
  "profylaxis", "severe_aki", "CRP_entry_by100",
  "past_urol_instrumentation", "immunosuppression_regimen",
  "depletion_induction_or_rejection_treatment_6M", "calendar_period"
)
ccw_bm_br_vars <- c(
  "fever_before_planned_ATB_stop",
  "clinical_worsening_before_planned_ATB_stop",
  "urine_findings_worsening_before_planned_ATB_stop",
  "ATB_extension_CRP_dynamics",
  "ATB_extension_other_reason",
  "ATB_extension_urologic_procedure"
)
ccw_variables <- c(
  "ID", "ATB_sensitivity_duration", "treatment_under14D",
  ccw_baseline_vars, ccw_bm_br_vars,
  ccw_outcomes
)

ccw_missing <- ccw_input |>
  dplyr::summarise(
    dplyr::across(
      all_of(ccw_variables),
      ~ sum(is.na(.x))
    )
  ) |>
  tidyr::pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "missing_n"
  ) |>
  dplyr::mutate(
    missing_percent = 100 * missing_n / nrow(ccw_input)
  ) |>
  dplyr::arrange(desc(missing_n)) |>
  data.frame()
kableExtra::kable(
  ccw_missing,
  digits = 1,
  caption = "Missing values in variables used by the CCW analysis. missing_n is the number of patients with NA; missing_percent is their percentage of the analysed cohort. Counts can overlap across variables. The agreed exclusion for missing entry CRP has already been applied"
)

ccw_sample <- ccw_input |>
  dplyr::summarise(
    patients_available = sum(lubridate::year(data_analysis$T0) >= 2017),
    excluded_missing_CRP = sum(
      lubridate::year(data_analysis$T0) >= 2017 & is.na(data_analysis$CRP_entry)
    ),
    patients_included = dplyr::n(),
    patients_with_any_NA = sum(dplyr::if_any(
      all_of(ccw_variables),
      is.na
    ))
  ) |>
  dplyr::mutate(
    patients_without_NA = patients_included - patients_with_any_NA
  ) |>
  data.frame()
kableExtra::kable(
  ccw_sample,
  caption = "Analysis sample. patients_available counts the original 2017+ cohort; excluded_missing_CRP counts patients excluded for missing entry CRP; patients_included counts those retained. patients_with_any_NA and patients_without_NA count retained patients with and without missing analysis inputs, respectively"
)
```


## Stopping by day 13

Model stopping by day 13 using the baseline and BM–BR covariates. The reference calendar period in this cohort is 2017–2021

```{r}
m_stop_by13 <- glm(
  treatment_under14D ~
    sex_female +
    age_by30y +
    log2_TX_to_infection +
    diabetes_severe +
    mra_positive +
    hemoculture_positive +
    profylaxis +
    severe_aki +
    CRP_entry_by100 +
    past_urol_instrumentation +
    immunosuppression_regimen +
    depletion_induction_or_rejection_treatment_6M +
    calendar_period +
    fever_before_planned_ATB_stop +
    clinical_worsening_before_planned_ATB_stop +
    urine_findings_worsening_before_planned_ATB_stop +
    ATB_extension_CRP_dynamics +
    ATB_extension_other_reason +
    ATB_extension_urologic_procedure,
  data = ccw_input,
  family = binomial(link = "logit")
)
summary(m_stop_by13)

kableExtra::kable(
  data.frame(
    supplied = nrow(ccw_input),
    used = nobs(m_stop_by13),
    omitted = nrow(ccw_input) - nobs(m_stop_by13)
  ),
  caption = "Two-period stopping model: observations used. supplied and used count patients available and used in fitting; omitted is their difference"
)
sjPlot::tab_model(
  m_stop_by13,
  pred.labels = unname(
    my_labels_dict[names(coef(m_stop_by13))]
  ),
  show.ci = 0.95,
  show.p = TRUE,
  show.se = FALSE,
  digits = 3,
  title = "Probability model for stopping sensitivity ATB treatment by day 13. OR states how many times the odds of stopping change per one modelled unit increase or a change from 0 to 1; categorical effects are relative to the reference level. Intervals are 95% profile-likelihood limits and p-values are Wald tests"
)
```

## Weight the two periods

Calculate inverse-probability weights

```{r}
ccw_period_data <- ccw_input

ccw_period_data$p_short <- as.numeric(predict(
  m_stop_by13,
  newdata = ccw_period_data,
  type = "response"
))
ccw_endpoints_period <- ccw_period_data |>
  dplyr::mutate(
    strategy = dplyr::if_else(
      treatment_under14D == 1,
      "short",
      "long"
    ),
    weight = dplyr::if_else(
      treatment_under14D == 1,
      1 / p_short,
      1 / (1 - p_short)
    )
  ) |>
  data.frame()
```
Check weights and effective sample sizes

```{r}
weight_issues_period <- ccw_endpoints_period |>
  dplyr::filter(!is.finite(weight)) |>
  dplyr::mutate(
    issue = dplyr::case_when(
      is.na(p_short) ~ "Missing stopping prediction",
      TRUE ~ "Non-finite inverse-probability weight"
    )
  ) |>
  dplyr::select(
    ID,
    strategy,
    ATB_sensitivity_duration,
    CRP_entry_by100,
    p_short,
    weight,
    issue
  ) |>
  data.frame()
kableExtra::kable(
  weight_issues_period,
  digits = 3,
  caption = "Two-period approximation: patients with unavailable or infinite weights. ID is the analysis identifier; strategy is short or long treatment; ATB_sensitivity_duration is treatment duration in days; CRP_entry_by100 is entry CRP divided by 100; p_short is the predicted probability of stopping by day 13; weight is the final inverse-probability weight. issue distinguishes a missing prediction from another non-finite weight. An empty table means no such issues"
)

weight_summary_period <- ccw_endpoints_period |>
  dplyr::group_by(strategy) |>
  dplyr::summarise(
    patients = dplyr::n(),
    nonfinite_weights = sum(!is.finite(weight)),
    median_weight = median(weight[is.finite(weight)]),
    p99_weight = quantile(
      weight[is.finite(weight)], 0.99, na.rm = TRUE
    ),
    max_weight = quantile(
      weight[is.finite(weight)], 1, na.rm = TRUE
    ),
    ESS = sum(weight)^2 / sum(weight^2),
    .groups = "drop"
  ) |>
  data.frame()
kableExtra::kable(
  weight_summary_period,
  digits = 3,
  caption = "Two-period approximation: weight diagnostics. patients counts retained patients by strategy; nonfinite_weights counts undefined or infinite weights; median_weight, p99_weight and max_weight describe finite weights only. ESS is the squared sum of all weights divided by their sum of squares and is undefined if any weight is missing or infinite. No patient is excluded by this diagnostic summary"
)
```

## Weighted recurrence risks

Show weighted risks

```{r}
ccw_point_period <- ccw_risks(ccw_endpoints_period)

kableExtra::kable(
  ccw_point_period,
  digits = 3,
  caption = "Two-period approximation: recurrence after therapy completion. outcome identifies the 30-day or 90-day window; short and long are weighted risks after <=13 and >13 days of sensitivity ATB treatment. risk_difference is short minus long; risk_ratio is short divided by long"
)
```

## Patient bootstrap

Refit the stopping model and calculate risks in each patient resample

```{r}
bootstrap_ccw_period <- function() {
  sampled <- sample.int(nrow(ccw_input), replace = TRUE)
  boot_data <- ccw_input[sampled, , drop = FALSE]
  boot_data$ID <- as.character(seq_len(nrow(boot_data)))
  m_stop_boot <- update(m_stop_by13, data = boot_data)
  if (!m_stop_boot$converged) {
    stop("Period-level stopping model did not converge in this replicate.")
  }
  boot_data$p_short <- predict(
    m_stop_boot,
    newdata = boot_data,
    type = "response"
  )
  endpoints <- boot_data |>
    dplyr::mutate(
      strategy = dplyr::if_else(
        treatment_under14D == 1,
        "short",
        "long"
      ),
      weight = dplyr::if_else(
        treatment_under14D == 1,
        1 / p_short,
        1 / (1 - p_short)
      )
    ) |>
    data.frame()
  ccw_risks(endpoints)
}
```
Run 500 patient bootstrap replicates, reusing the existing cache if present

```{r}
modelac <- "ccw_results_v2_d13minusVSsd14plus_2017plus"

run2(
  modelac,
  expr = {
    set.seed(seeding)
    purrr::map(seq_len(500), function(replicate_id) {
      tryCatch(
        list(
          result = bootstrap_ccw_period(),
          error = NA_character_
        ),
        error = function(e) list(
          result = ccw_point_period |>
            dplyr::mutate(
              dplyr::across(
                c(short, long, risk_difference, risk_ratio),
                ~ NA_real_
              )
            ) |>
            data.frame(),
          error = conditionMessage(e)
        )
      )
    })
  }
)

ccw_bootstrap_period <- get(modelac)

bootstrap_errors_period <- purrr::map_chr(
  ccw_bootstrap_period,
  "error"
)
bootstrap_status_period <- data.frame(
  requested = length(ccw_bootstrap_period),
  failed = sum(!is.na(bootstrap_errors_period))
)
kableExtra::kable(
  bootstrap_status_period,
  caption = "Two-period approximation: bootstrap execution. requested counts patient resamples; failed counts model-fitting errors or nonconvergence. Non-finite risk estimates are accounted for in valid_replicates in the results table"
)

unique(bootstrap_errors_period[!is.na(bootstrap_errors_period)])

bootstrap_results_period <- purrr::map_dfr(
  ccw_bootstrap_period,
  "result",
  .id = "replicate"
) |>
  data.frame()
```

Show estimates and percentile 95% confidence intervals

```{r}
bootstrap_limits_period <- bootstrap_results_period |>
  tidyr::pivot_longer(
    cols = c(short, long, risk_difference, risk_ratio),
    names_to = "estimand",
    values_to = "estimate"
  ) |>
  dplyr::group_by(
    outcome,
    estimand
  ) |>
  dplyr::summarise(
    valid_replicates = sum(is.finite(estimate)),
    lower = quantile(estimate[is.finite(estimate)], 0.025, na.rm = TRUE),
    upper = quantile(estimate[is.finite(estimate)], 0.975, na.rm = TRUE),
    .groups = "drop"
  ) |>
  data.frame()
ccw_table_period <- ccw_point_period |>
  tidyr::pivot_longer(
    cols = c(short, long, risk_difference, risk_ratio),
    names_to = "estimand",
    values_to = "estimate"
  ) |>
  dplyr::left_join(
    bootstrap_limits_period,
    by = c("outcome", "estimand")
  ) |>
  dplyr::mutate(
    lower = dplyr::if_else(is.finite(estimate), lower, NA_real_),
    upper = dplyr::if_else(is.finite(estimate), upper, NA_real_)
  ) |>
  data.frame()
kableExtra::kable(
  ccw_table_period,
  digits = 3,
  caption = "Two-period approximation: recurrence estimates after therapy completion. outcome identifies the 30-day or 90-day window; estimand identifies the short-treatment risk, long-treatment risk, risk difference (short minus long) or risk ratio (short divided by long). estimate is the point estimate; lower and upper are patient-bootstrap percentile 95% confidence limits. valid_replicates counts finite bootstrap estimates contributing to each interval"
)
```

# Reproducibility

```{r}
sessionInfo()
```


